### 2021-01-08 paper/main.tex
updated code and documentation

%%%%%%%% ICML 2021 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2021} with \usepackage[nohyperref]{icml2021} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2021}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2021}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{OpReg-Boost}

\begin{document}

\twocolumn[
\icmltitle{OpReg-Boost: Learning to Accelerate Online Algorithms \\ with Operator Regression}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2021
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Nicola Bastianello}{unipd}
\icmlauthor{Andrea Simonetto}{ibm}
\icmlauthor{Emiliano Dall'Anese}{cu}
\end{icmlauthorlist}

\icmlaffiliation{unipd}{Department of Information Engineering (DEI), University of Padova, Padova, Italy}
\icmlaffiliation{ibm}{IBM Research Europe, Dublin, Ireland}
\icmlaffiliation{cu}{Department of Electrical, Computer, and Energy Engineering (ECEE), University of Colorado Boulder, Boulder, Colorado, USA}

\icmlcorrespondingauthor{Nicola Bastianello}{nicola.bastianello.3@phd.unipd.it}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{optimization, online optimization, operator theory, regression, acceleration}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
In this paper we propose a learning-based acceleration scheme for online optimization. .... novel operator regression ...
\end{abstract}

% ------------------------------------------------------------------------------
\section{Introduction}\label{sec:introduction}

.... problem formulation, literature review, contribution statement .....

% ------------------------------------------------------------------------------
\section{Operator Regression}\label{sec:opreg}

.... operator regression, application to accelerate optimization algorithm, interpolation version, and autotuning, PRS solver (in appendix) ....

% ------------------------------------------------------------------------------
\section{OpReg-Boost}\label{sec:online-opreg}

.... application of OpReg to online optimization ....

% ------------------------------------------------------------------------------
\section{Numerical Results}\label{sec:numerical}

.... simulation setup, reference to code (for now in supplementary materials), simulations ....

%% FIGURE
%\begin{figure}[ht]
%\vskip 0.2in
%\begin{center}
%\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
%\caption{Historical locations and number of accepted papers for International
%Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
%Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
%produced, the number of accepted papers for ICML 2008 was unknown and instead
%estimated.}
%\label{icml-historical}
%\end{center}
%\vskip -0.2in
%\end{figure}

%% ALGORITHM
%\begin{algorithm}[tb]
%   \caption{Bubble Sort}
%   \label{alg:example}
%\begin{algorithmic}
%   \STATE {\bfseries Input:} data $x_i$, size $m$
%   \REPEAT
%   \STATE Initialize $noChange = true$.
%   \FOR{$i=1$ {\bfseries to} $m-1$}
%   \IF{$x_i > x_{i+1}$}
%   \STATE Swap $x_i$ and $x_{i+1}$
%   \STATE $noChange = false$
%   \ENDIF
%   \ENDFOR
%   \UNTIL{$noChange$ is $true$}
%\end{algorithmic}
%\end{algorithm}

%% TABLE
%\begin{table}[t]
%\caption{Classification accuracies for naive Bayes and flexible
%Bayes on various data sets.}
%\label{sample-table}
%\vskip 0.15in
%\begin{center}
%\begin{small}
%\begin{sc}
%\begin{tabular}{lcccr}
%\toprule
%Data set & Naive & Flexible & Better? \\
%\midrule
%Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
%Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
%Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
%Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
%Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
%Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
%Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
%Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
%\bottomrule
%\end{tabular}
%\end{sc}
%\end{small}
%\end{center}
%\vskip -0.1in
%\end{table}

\bibliography{main}
\bibliographystyle{icml2021}

%TODO: keep appendices in supplementary material only
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

\section{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019 and 2021. Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2021-01-08 reg4opt/interpolation.py

@@ -1,6 +1,10 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
 
+"""
+Interpolation of Lipschitz continuous operators.
+"""
+
 import numpy as np
 from numpy import linalg as la
 
@@ -13,9 +17,31 @@ from reg4opt import utils
 
 #%% INTERPOLATION
 
-def interpolator(x, x_i, t_i, zeta, t0=None):
-    """
+def interpolator(x, x_i, t_i, zeta, t0=None, solver=None, **solver_params):
+    r"""
     Operator interpolation.
+    
+    This function interpolates the :math:`\zeta`-Lipschitz continuous operator
+    :math:`\mathcal{T} : \mathbb{R}^n \to \mathbb{R}^n` to the point :math:`x`,
+    preserving the Lipschitz continuity.
+    
+    In particular, given the operator evaluations
+    
+    .. math:: t_i = \mathcal{T} x_i, \quad i = 1, \ldots, D
+    
+    the function computes :math:`\hat{\mathcal{T}} x` as
+    
+    .. math:: \hat{\mathcal{T}} x = \begin{cases}
+                  t_i & \text{if} \ x = x_i \\
+                  \hat{t} \in \bigcap_{i \in [D]} \mathbb{B}_{\zeta \|x - x_i\|}(t_i) & \text{otherwise}
+              \end{cases}
+    
+    where :math:`\mathbb{B}_{\zeta \|x - x_i\|}(t_i)` is a ball of center 
+    :math:`t_i` and radius :math:`\zeta \|x - x_i\|`. We see then that 
+    interpolating requires finding a point in the intersection of balls. To 
+    this end, an efficient approach is to use the method of alternating 
+    projections (MAP) (see `alternating_projections`), but other solvers are
+    available.
 
     Parameters
     ----------
@@ -30,11 +56,28 @@ def interpolator(x, x_i, t_i, zeta, t0=None):
     t0 : array_like, optional
         The initial condition for the projection algorithm, defaults to a 
         vector of zeros.
+    solver : str
+        The method that should be used to find a point in the intersection of
+        balls. By default the MAP is used, due to its efficiency in this 
+        scenario.
+    solver_params : tuple
+        Parameters for the solver, for example the maximum number of iterations
+        that it can perform.
 
     Returns
     -------
     ndarray
         The interpolated operator evaluated at `x`.
+    
+    See Also
+    --------
[…]

### 2021-01-08 reg4opt/operators.py

@@ -1,9 +1,9 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
+
 """
 Operator template and examples.
 """
-
 
 import numpy as np
 from numpy import linalg as la
@@ -22,8 +22,31 @@ class Operator():
     where :math:`\mathbb{D}_i \subset \mathbb{R}^{n_{i,1} \times n_{i,2} \times \cdots}`
     for some given dimensions :math:`n_{i,1}, n_{i,2}, \ldots`, :math:`i = 1, 2`.
     
+    `Operator` objects support the following operations:
+        
+        - composition,
+        - averaging (a.k.a. relaxation),
+        - addition,
+        - product by a scalar.
     
-    TODO: operations: sum of operators, product by scalar, composition, averaging
+    An `Operator` should expose the `operator` method to perform evaluations
+    of :math:`\mathcal{T}`. The class then implements the `fpr` which computes
+    the fixed point residual :math:`\| \mathcal{T} x - x\|` at a given point
+    :math:`x`.
+    
+    The `Operator` can also be time-varying, in which case the function 
+    `sample` is also available.
+    
+    Attributes
+    ----------
+    dom : tvopt.sets.Set
+        The operator's domain.
+    rng : tvopt.sets.Set
+        The operator's range.
+    time : tvopt.sets.T
+        The time domain :math:`\mathbb{R}_+`. If the cost is static this is None.
+    is_dynamic : bool
+        Attribute to check if the cost is static or dynamic.
     """
     
     def __init__(self, dom, rng=None, time=None):
@@ -64,6 +87,10 @@ class Operator():
     def fpr(self, x, *args, **kwargs):
         """
         Evaluate the fixed point residual (FPR).
+        
+        This method returns the FPR
+        
+        .. math:: \| \mathcal{T} x - x \|.
 
         Parameters
         ----------
@@ -72,6 +99,8 @@ class Operator():
         *args
             The time at which the operator should be evaluated. Not required if
             the operator is static.
+        **kwargs
+            Any other required argument.
 
         Returns
         -------
@@ -83,41 +112,79 @@ class Operator():
     
     def compose(self, other):
         """
-        TODO
+        Compose the operator with a second one.
+        
+        The method composes the operator with a second one, provided that the
+        range of the former coincides with the domain of the latter.
 
         Parameters
         ----------
-        other : TYPE
-            DESCRIPTION.
+        other : Operator
[…]

### 2021-01-08 reg4opt/regression.py

@@ -2,7 +2,7 @@
 # -*- coding: utf-8 -*-
 
 """
-Convex and operator regression methods.
+Operator regression with different solvers.
 """
 
 import math
@@ -14,26 +14,67 @@ ran = default_rng()
 
 from reg4opt import utils 
 
-#TODO
-# - document and comment (say that the data should be column numpy array)
-
 
 #%% OPERATOR REGRESSION
 
-# def operator_regression(x, y, c, autotune=False, solver="CVXPY", **solver_params):
+def operator_regression(x, y, c, autotune=False, solver="PRS", **solver_params):
+    r"""
+    Operator regression.
     
-#     solver = solver.strip().lower()
+    The function solves an operator regression problem
     
-#     if solver == "cvxpy" or solver == "c" or solver == "cp":
-#         return cvxpy_solver(x, y, c, autotune, **solver_params)
+    .. math:: \begin{align}
+                  &\min_{t_i, \ i \in [D]} \frac{1}{D} \sum_{i = 1}^D \| t_i - y_i \|^2 \\
+                  &\text{s.t.} \ \| t_i - t_j \|^2 \leq \zeta^2 \| y_i - y_j \|^2
+              \end{align}
     
-#     elif solver == "prs" or solver == "p":
-#         if not autotune:
-#             return prs_solver(x, y, c, **solver_params), c
-#         else:
-#             return prs_solver_autotuning(x, y, c, **solver_params)
+    where :math:`y_i = \mathcal{T} x_i`, :math:`i = 1, \ldots, D`, are 
+    evaluations of the operator to be aproximated, and :math:`\zeta \in (0, 1]`
+    is the Lipschitz continuity modulus for the approximated operator.
+    
+    The function can also be used to solve the *autotuned* version of the
+    operator regression problem, in which the Lipschitz modulus becomes an
+    unknown of the problem:
+    
+    .. math:: \begin{align}
+                  &\min_{t_i, \ i \in [D]} \frac{1}{D} \sum_{i = 1}^D \| t_i - y_i \|^2 + \frac{w}{2} z^2 \\
+                  &\text{s.t.} \ \| t_i - t_j \|^2 - z \| y_i - y_j \|^2 \leq 0
+              \end{align} 
+              
+    for some :math:`w > 0`.
+    
+    The function can use two different solvers, one based on `cvxpy` (which, 
+    being more general purpose in general is less efficient), and a tailored
+    solver based on the Peaceman-Rachford splitting method.
+    
[…]

### 2021-01-08 reg4opt/solvers.py

@@ -1,7 +1,8 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
+
 """
-Utility functions.
+Solvers.
 """
 
 import numpy as np
@@ -15,12 +16,57 @@ from tvopt.solvers import stop
 from collections import deque as queue
 
 
+#%% SOLVERS FOR SMOOTH PROBLEMS
 
 def nesterov_gradient(problem, step, inertia, x_0=0, num_iter=100, tol=None):
     r"""
+    Nesterov gradient method.
+    
+    This function implements the Nesterov accelerated gradient described by the
+    following equations, for :math:`\ell \in \mathbb{N}`:
+    
+    .. math:: \begin{align}
+                  x^{\ell+1} &= x^\ell - \alpha \nabla f(y^\ell) + \beta (x^\ell - x^{\ell-1}) \\
+                  y^{\ell+1} &= x^{\ell+1} + \beta (x^{\ell+1} - x^{\ell})
+              \end{align}
+    
+    where :math:`\alpha` and :math:`\beta` are the step-size and inertial
+    coefficient, respectively, and where :math:`y^0 = x^0`.
+
+    Parameters
+    ----------
+    problem : dict
+        A dictionary containing the problem data, in particular the cost
+        function "f".
+    step : float
+        The step-size for the method.
+    inertia : float
+        The inertial coefficient for the method.
+    x_0 : array_like, optional
+        The initial condition. This can be either an ndarray of suitable size,
+        or a scalar. If it is a scalar then the same initial value is used for
+        all components of :math:`x`.
+    num_iter : int, optional
+        The number of iterations to be performed.
+    tol : float, optional
+        If given, this argument specifies the tolerance :math:`t` in the 
+        stopping condition :math:`\| x^{\ell+1} - x^\ell \| \leq t`.
+
+    Returns
+    -------
+    x : ndarray
+        The (approximate) solution.
+    
+    References
+    ----------
+    .. [#] Y. Nesterov, Lectures on Convex Optimization, vol. 137. Cham: 
+           Springer International Publishing, 2018.
     """
     
+    # unpack the problem
     f = problem["f"]
+    
+    # initialization
     x = np.zeros(f.dom.shape)
     x[...] = x_0
     x_old = x_0
@@ -29,6 +75,7 @@ def nesterov_gradient(problem, step, inertia, x_0=0, num_iter=100, tol=None):
     
     for l in range(num_iter):
         
[…]

### 2021-01-08 reg4opt/utils.py

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
+
 """
 Utility functions.
 """
@@ -17,13 +18,74 @@ from tvopt import sets
 
 #%% DATA GENERATION FOR OPERATOR REGRESSION
 
-def generate_data(T, x, num_data, var):
+def generate_data(T, x, num_data, method="normal", **kwargs):
+    """
+    Generate the training data for an operator regression problem.
+    
+    The function encapsulates different method of generating the training data
+    for an operator regression problem. The choices are
+    
+    * normal: the data are chosen as :math:`x + d_i`, where
+      :math:`d_i` are random vectors with normal distribution;
+    * fireworks: the data are chosen as :math:`x + d_i`, where we have
+      :math:`d_i = a e_j`, with :math:`a` a r.v. with normal distribution and
+      :math:`e_j` a randomly selected vector of the standard basis;
+    * uniform: the data are chosen as :math:`x + d_i`, where
+      :math:`d_i` are random vectors with uniform distribution.
+
+    Parameters
+    ----------
+    T : operators.Operator
+        The operator source of the training data.
+    x : ndarray
+        The center of the training data, that is, all other training points are
+        chosen as perturbations of `x`.
+    num_data : int
+        The number of training points, including `x`, which means that 
+        `num_data`-1 points are randomly selected.
+    method : str, optional
+        The method to choose the training points, defaults to "normal".
+    **kwargs : tuple
+        The arguments of `method`.
+
+    Returns
+    -------
+    list
+        The points :math:`x_i` selected by the method.
+    list
+        The operator `T` evaluated in the chosen points.
+    
+    See Also
+    --------
+    generate_data_n : Data generation with normal distribution.
+    generate_data_fw : Data generation with fireworks method.
+    generate_data_u : Data generation with unform distribution.
+    """
+    
+    if method == "normal" or method == "n":
+        return generate_data_n(T, x, num_data, **kwargs)
+    elif method == "fireworks" or method == "fw" or method == "f":
+        return generate_data_fw(T, x, num_data, **kwargs)
+    elif method == "uniform" or method == "u":
+        return generate_data_fw(T, x, num_data, **kwargs)
+    else:
+        return generate_data_n(T, x, num_data, **kwargs)
+
+def generate_data_n(T, x, num_data, var):
[…]

### 2021-01-08 reg4opt/solvers.py
added solvers

@@ -5,6 +5,7 @@
 Solvers.
 """
 
+import math
 import numpy as np
 from numpy import linalg as la
 
@@ -92,9 +93,80 @@ def nesterov_gradient(problem, step, inertia, x_0=0, num_iter=100, tol=None):
 
 #%% ACCELERATION SCHEMES FOR OPERATORS
 
-# def fista:
+def fista(problem, step, x_0=0, num_iter=100, tol=None):
+    r"""
+    Fast iterative shrinkage.thresholding algorithm (FISTA).
+    
+    The function implements FISTA for solving the composite problem
+    :math:`\min_x f(x) + g(x)`, with :math:`f` smooth. The algorithm is
+    defined as follows, for :math:`\ell \in \mathbb{N}`:
+    
+    .. math:: \begin{align}
+                  x^{\ell+1} &= \operatorname{prox}_{\alpha g}(y^\ell - \alpha \nabla f(y^\ell)) \\
+                  t^{\ell+1} &= \frac{1 + \sqrt{4 (t^\ell)^2 + 1}}{2} \\
+                  y^{\ell+1} &= x^{\ell+1} + \frac{t^\ell - 1}{t^{\ell+1}} (x^{\ell+1} - x^\ell)
+              \end{align}
+    
+    where :math:`\alpha` is an appropriate step-size, and :math:`y^1 = x^0`,
+    :math:`t^1 = 1`. See [#]_ for details and convergence.
 
+    Parameters
+    ----------
+    problem : dict
+        A dictionary containing the problem data, in particular the cost
+        functions "f" and "g".
+    step : float
+        The step-size for the method.
+    x_0 : array_like, optional
+        The initial condition. This can be either an ndarray of suitable size,
+        or a scalar. If it is a scalar then the same initial value is used for
+        all components of :math:`x`.
+    num_iter : int, optional
+        The number of iterations to be performed.
+    tol : float, optional
+        If given, this argument specifies the tolerance :math:`t` in the 
+        stopping condition :math:`\| x^{\ell+1} - x^\ell \| \leq t`.
 
+    Returns
+    -------
+    x : ndarray
+        The (approximate) solution.
+    
+    References
+    ----------
+    .. [#] A. Beck and M. Teboulle, "A Fast Iterative Shrinkage-Thresholding 
+           Algorithm for Linear Inverse Problems," SIAM Journal on Imaging 
[…]

### 2021-01-08 reg4opt/solvers.py
updated solvers

@@ -12,9 +12,13 @@ from numpy import linalg as la
 from numpy.random import default_rng
 ran = default_rng()
 
+from collections import deque as queue
+
+from reg4opt import utils
+
 from tvopt.solvers import stop
 
-from collections import deque as queue
+
 
 
 #%% SOLVERS FOR SMOOTH PROBLEMS
@@ -157,6 +161,54 @@ def fista(problem, step, x_0=0, num_iter=100, tol=None):
         
         # proximal gradient step
         x = g.proximal(y - step*f.gradient(y), step)
+        
+        if stop(x, x_old, tol): break
+    
+        # inertial coefficient
+        t_old = t
+        t = (1 + math.sqrt(t**2 + 1)) / 2
+        # inertial step
+        y = x + ((t_old-1)/t)*(x - x_old)
+    
+    return x
+
+def backtracking_fista(problem, b, x_0=0, num_iter=100, tol=None):
+    r"""
+
+    """
+    
+    # unpack the problem
+    f, g = problem["f"], problem["g"]
+    
+    # initialization
+    x = np.zeros(f.dom.shape)
+    x[...] = x_0
+    
+    y = x_0
+    t = 1 # for inertial coefficient
+    
+    
+    for l in range(num_iter):
+        
+        # store past iterate
+        x_old = x
+        
+        # backtracking line search
+        a = 1
+        stop = False
+        while not stop:
+            
+            p_l = g.proximal(y - a*f.gradient(y), a)
+            
+            if f.function(p_l) <= \
+               f.function(y) + (p_l - y).T.dot(f.gradient(y)) \
+               + (1/(2*a))*utils.square_norm(p_l - y):
+                stop = True
+            else:
+                a = b*a
+        
+        # proximal gradient step
+        x = p_l
         
         if stop(x, x_old, tol): break
     

### 2021-01-08 reg4opt/solvers.py
updated solvers

@@ -19,8 +19,6 @@ from reg4opt import utils
 from tvopt.solvers import stop
 
 
-
-
 #%% SOLVERS FOR SMOOTH PROBLEMS
 
 def nesterov_gradient(problem, step, inertia, x_0=0, num_iter=100, tol=None):

### 2021-01-08 reg4opt/regression.py
updated documentation

@@ -302,8 +302,6 @@ def qcqp(p_0, q_0, P, r,
         The (approximate) dual solution.
     """
     
-    # p_0 is the diagonal element of P_0
-    
     n = q_0.size//2 # domain dimension
     
     # compute P^-1(l) and P^-1(l) q(l)
@@ -546,8 +544,6 @@ def qcqp_autotuning(p_0_1, p_0_2, q_0, P, q,
     l : float
         The (approximate) dual solution.
     """
-    
-    # p_0 is the diagonal element of P_0
     
     n = q_0.size//2 # domain dimension
     

### 2021-01-08 reg4opt/solvers.py
updated solvers

@@ -298,7 +298,8 @@ def anderson_acceleration(problem, m, x_0=None, num_iter=100, tol=None):
         m_l = min(m, l)
         
         # compute residuals
-        R = np.hstack([np.reshape(T.operator(x_old[-i])-x_old[-i], (-1,1)) for i in range(1, m_l+1)])
+        # R = np.hstack([np.reshape(T.operator(x_old[-i])-x_old[-i], (-1,1)) for i in range(1, m_l+1)])
+        R = np.hstack([T.operator(x_old[-i])-x_old[-i] for i in range(1, m_l+1)])
 
         # compute extrapolation coefficients
         if m_l == 1:

### 2021-01-08 reg4opt/utils.py
updated utils

@@ -71,7 +71,7 @@ def generate_data(T, x, num_data, method="normal", **kwargs):
     else:
         return generate_data_n(T, x, num_data, **kwargs)
 
-def generate_data_n(T, x, num_data, var):
+def generate_data_n(T, x, num_data, var=1):
     """
     Data generation using perturbation that are normally distributed with
     variance `var`. See `generate_data` for details.
@@ -81,7 +81,7 @@ def generate_data_n(T, x, num_data, var):
     
     return x_i, [T.operator(z) for z in x_i]
 
-def generate_data_fw(T, x, num_data, var):
+def generate_data_fw(T, x, num_data, var=1):
     """
     Data generation using perturbation chosen according to the fireworks
     method. See `generate_data` for details.
@@ -96,7 +96,7 @@ def generate_data_fw(T, x, num_data, var):
     
     return x_i, [T.operator(z) for z in x_i]
 
-def generate_data_u(T, x, num_data, a):
+def generate_data_u(T, x, num_data, a=1):
     """
     Data generation using perturbation that are uniformly distributed with
     range -`a` to `a`. See `generate_data` for details.

### 2021-01-08 examples/test_alternating_projections.py
added test of alternating projections

@@ -1,0 +1,151 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+
+import numpy as np
+from numpy import linalg as la
+
+from numpy.random import default_rng
+ran = default_rng()
+
+import sys
+sys.path.append("..")
+
+from reg4opt import utils
+
+
+# plots setup
+import matplotlib.pyplot as plt
+    
+plt.rc("text", usetex=True)
+plt.rc("font", family="serif")
+plt.rc("text.latex", preamble=r"\usepackage{bm,fixmath,amssymb}")
+fontsize = 18
+
+
+def alternating_projections(s, x, tol=1e-10, num_iters=1000):
+    """
+    Implementation of the method of alternating projections (MAP) that only 
+    returns the number of iterations required to reach convergence. See
+    `alternating_projections` in `reg4opt.interpolation` for documentation.
+    """
+    
+    x_old = np.copy(x)
+    
+    for k in range(num_iters):
+    
+        for i in range(len(s)):
+            
+            x = s[i].projection(x)
+            
+        # check stopping condition
+        if la.norm(x - x_old) <= tol: break
+        else: x_old = np.copy(x)
+    
+    return k
+
+
+
+save_fig = False
+
+
+#%% HISTOGRAM
+
+# ------ problem formulation
+# domain dimensions and num. of balls
+n = 25
+d = 100
+
+reps = 10
+
+# initial condition
+x0 = 1e10*ran.standard_normal((n,1))
+
+
+# ------ alternating projections
+results = []
+
+for l in range(reps):
+
+    # generate the balls
+    s = utils.random_intersecting_balls(n, d)
+    
+    # apply alternating projections        
+    k = alternating_projections(s, x0, tol=1e-15)
+    
+    results.append(k)
+    
+    utils.print_progress(l+1, reps)
+
+
+# ------ results
+print("Max. num. of iterations {}".format(max(results)))
+print("Mean num. of iterations {} +/- {}".format(np.mean(results), np.std(results)))
+   
+
+plt.figure()
+
+plt.hist(results, bins=max(results), rwidth=0.8)
+
+plt.grid()
+plt.xlabel("Num. of iterations", fontsize=fontsize)
+plt.ylabel("Num. of occurrences", fontsize=fontsize)
+    
+if save_fig: plt.savefig("images/MAP_histogram.pdf", bbox_inches="tight")
[…]

### 2021-01-08 examples/alternating_projections.py
added self-contained examples

@@ -1,6 +1,11 @@
 #!/usr/bin/env python3
 # -*- coding: utf-8 -*-
 
+"""
+Test the alternating projection method (MAP) for finding a point in the
+intersection of ball sets.
+"""
+
 import numpy as np
 from numpy import linalg as la
 

### 2021-01-08 examples/online_linear_regression.py

@@ -1,0 +1,305 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+
+"""
+Solve an online linear regression problem with l1 regularization, comparing
+the operator regression solver with other methods.
+"""
+
+import numpy as np
+from numpy import linalg as la
+from numpy.random import default_rng
+ran = default_rng()
+
+import sys
+sys.path.append("..")
+
+from tvopt.utils import random_matrix
+from tvopt import costs, solvers
+
+from reg4opt.operators import Gradient, Proximal
+from reg4opt.regression import operator_regression
+from reg4opt.interpolation import interpolator
+from reg4opt.utils import print_progress, generate_data
+from reg4opt.solvers import fista, anderson_acceleration
+
+
+
+#%% SET-UP
+
+n = 10 # domain dimension
+t_s, t_max = 0.1, 1 # sampling time and time horizon
+
+
+# ------ signal
+omega = 3 # angular velocity
+phi = np.pi*ran.random(n) # phase
+shift = 10*ran.random(n) # shift the signals away from the origin
+
+# generate signal
+s = np.zeros((n, int(t_max/t_s)))
+for i in range(n):
+    s[i,:] = np.sin(omega*np.arange(0,t_max,t_s) + phi[i]) + shift[i]
+
+# sparsify signal
+sparsity = int(n/3)
+
+idx_z = ran.choice(range(n), sparsity, False)
+s[idx_z,:] = 0
+
+# ------ observation noise
+noise_var = 1e-4
+noise = np.sqrt(noise_var)*ran.standard_normal(s.shape)
+
+
+# ------ regression cost
+# choose condition number
+L, mu = 1e8, 1
+
+# observation matrix
+rk = n//2
+A = random_matrix(np.sqrt(np.hstack((L, (L-mu)*ran.random(rk-2)+mu, mu, np.zeros(n-rk)))))
+
+# observations
+b = A.dot(s) + noise
+
+
+# ------ generate cost and operator
+step = 2 / (L + mu) # gradient step-size
+w = 5 # weight of l1 norm
+
+# costs
+f = costs.DiscreteDynamicCost([costs.LinearRegression(A, b[:,[k]]) for k in range(b.shape[1])], t_s=t_s)
+g = costs.Norm_1(n, w)
+
+# operators
+T = Gradient(f, step)
+P = Proximal(g, step)
+
+
[…]

### 2021-01-08 reg4opt/solvers.py

@@ -193,15 +193,15 @@ def backtracking_fista(problem, b, x_0=0, num_iter=100, tol=None):
         
         # backtracking line search
         a = 1
-        stop = False
-        while not stop:
+        s = False
+        while not s:
             
             p_l = g.proximal(y - a*f.gradient(y), a)
             
             if f.function(p_l) <= \
                f.function(y) + (p_l - y).T.dot(f.gradient(y)) \
                + (1/(2*a))*utils.square_norm(p_l - y):
-                stop = True
+                s = True
             else:
                 a = b*a
         

### 2021-01-11 examples/online_linear_regression.py
updated examples

@@ -28,7 +28,7 @@ from reg4opt.solvers import fista, anderson_acceleration
 #%% SET-UP
 
 n = 10 # domain dimension
-t_s, t_max = 0.1, 1 # sampling time and time horizon
+t_s, t_max = 0.1, 10 # sampling time and time horizon
 
 
 # ------ signal
@@ -91,7 +91,7 @@ rho = 1
 tol = 1.5*1e-4
 
 # parameter for Anderson acceleration (num. of past iterates in extrapolation)
-m = num_iter
+m = num_data
 
 
 # initial condition
@@ -153,13 +153,21 @@ t = 0
 
 for k in range(f.time.num_samples):
     
-    T_k = P.compose(T.sample(k*t_s)) # sampled operator
+    T_k = T.sample(k*t_s) # sampled operator
+        
+    for _ in range(num_iter):
+        
+        # Anderson acceleration on gradient
+        y = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_iter)
+        
+        # proximal step
+        y = g.proximal(y, step)
+        x_old.append(y)
     
-    # apply gradient step
-    x[...,k+1] = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_iter)
-
+    x[...,k+1] = y
+    
     # update list of past iterates
-    x_old = [x[...,k+1-i] for i in range(min(k+1, m))].reverse()
+    x_old = [x[...,k+1-i] for i in range(min(k+1, m))][::-1]
 
     print_progress(k+1, f.time.num_samples)
 
@@ -283,8 +291,8 @@ fontsize = 18
 markers = ['o', 's', 'v', '^', '*', 'D', 'H', '<', '>', 'p']
 
 
+# ------ tracking error over time
 time = np.arange(0, f.time.t_max, f.time.t_s)
-
 
 plt.figure()
 
@@ -301,5 +309,27 @@ plt.legend(fontsize=12)
 
 plt.xlabel("Time [s]", fontsize=fontsize)
 plt.ylabel("Tracking error", fontsize=fontsize)
+
+plt.show()
+
+
+# ------ cumulative tracking error per gradient calls
+time = np.arange(1, f.time.num_samples+1)
+
+plt.figure()
+
+plt.semilogy(num_iter*time, np.cumsum(err_pg)/time, label="Proximal gradient", marker=markers[0], markevery=50)
[…]

### 2021-01-11 paper/main.tex
updated paper

@@
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+\usepackage{amsmath,amssymb,amsthm}
+\usepackage{bm,fixmath}
+
+%-------------------- COMMANDS
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator{\prox}{prox}
+\DeclareMathOperator{\fix}{fix}
+
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
+
+% new math commands
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\R}{\mathbb{R}}
+
+\newcommand{\bv}{\mathbold{b}}
+\newcommand{\e}{\mathbold{e}}
+\newcommand{\p}{\mathbold{p}}
+\newcommand{\q}{\mathbold{q}}
+\newcommand{\tv}{\mathbold{t}}
+\newcommand{\x}{\mathbold{x}}
+\newcommand{\y}{\mathbold{y}}
+\newcommand{\vv}{\mathbold{v}}
+\newcommand{\z}{\mathbold{z}}
+\newcommand{\xx}{\pmb{\xi}}
+
+\newcommand{\Am}{\mathbold{A}}
+\renewcommand{\Im}{\mathbold{I}}
+\newcommand{\Pm}{\mathbold{P}}
+
+\newcommand{\I}{\mathcal{I}}
+\newcommand{\T}{\mathcal{T}}
+
+\newcommand{\Ts}{T_\mathrm{s}}
+
+\newcommand{\nicola}[1]{{\color{blue}#1}}
 
@@
 
-% ------------------------------------------------------------------------------
+%------------------------------------------------------------------------------
 \section{Introduction}\label{sec:introduction}
@@
 
-% ------------------------------------------------------------------------------
+%------------------------------------------------------------------------------
 \section{Operator Regression}\label{sec:opreg}
 
-.... operator regression, application to accelerate optimization algorithm, interpolation version, and autotuning, PRS solver (in appendix) ....
+%------------------------------------------------
+\subsection{Problem formulation}
+Consider the following \emph{convex, time-varying} optimization problem
+\begin{equation}\label{eq:continuous-time-problem}
+	\x^*(t) \in \argmin f(\x; t) + g(\x; t)
+\end{equation}
+where $f : \R^n \times \R_+ \to \R$ and $g : \R^n \times \R_+ \to \R \cup \{ +\infty \}$ are closed, convex and proper functions, optionally with $g \equiv 0$.
+In particular, we are interested in solving the following sequence of static problems derived from sampling~\eqref{eq:continuous-time-problem} at the times $\{ t_k \}_{k \in \N}$, $t_{k+1} - t_k = \Ts$:
+\begin{equation}\label{eq:base-problem}
+	\x^*(t) \in \argmin f(\x; t_k) + g(\x; t_k).
+\end{equation}
 
-% ------------------------------------------------------------------------------
+Problem~\eqref{eq:base-problem} is convex but not strongly so, which means that the performance of online algorithms applied to it is worse than the performance attainable for strongly convex problems.
+As an example, consider the case $g \equiv 0$, and apply an online gradient descent: if the problem is convex the (static) regret is $O(\sqrt{T})$, with $T$ the number of sampling times, while if the problem is strongly convex the regret is $O(\log(T))$, section~3.1 in \cite{hazan_introduction_2016}.
+\nicola{Instead of citing Hazan, we should derive a result in an appendix, for example for the fixed point residual}
+
+As we can see from the results just mentioned, in general in online optimization it is not possible to achieve zero regret, due to the dynamic nature of the problem.
+However, for strongly convex problems smaller regrets can be achieved.
+
+The goal then is to design learning techniques that allow to achieve strongly convex-like performance while tracking a solution trajectory of the problem~\eqref{eq:base-problem} with good accuracy.
+
+%------------------------------------------------
+\subsection{Operator regression}
+First of all, we define the observations
+$$
+	\y_i = \T_f \x_i + \e_i, \quad i \in [D]
+$$
+of the operator we want to regularize. Now, using Fact~2.2 in \cite{ryu_operator_2020} we know that an operator $\T$ is $\zeta$-contractive interpolable if and only if it satisfies
+$$
+	\norm{\T \x_i - \T \x_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2, \quad \forall i,j \in [D], \ i \neq j.
+$$
+Therefore, we can define the following constrained regression problem:
+\begin{equation}\label{eq:operator-regression}
+\begin{split}
+	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \ \forall i,j \in [D], i \neq j
+\end{split}
+\end{equation}
+where again the cost function is a least square terms on the observations and the constraints enforce contractiveness.
+
+\paragraph{Auto-tuning contraction}
+We can modify~\eqref{eq:operator-regression} by including $w = \zeta^2$ as an unknown of the regression problem, which becomes
+\begin{equation}
+\begin{split}
+	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 + \frac{c}{2} w^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 - w \norm{\x_i - \x_j}^2 \leq 0 \ \forall i,j \in [D], i \neq j
+\end{split}
+\end{equation}
+this way the contraction constant does not need to be specified, and is \emph{auto-tuned} by the regression.
+
+\paragraph{PRS-based solver}
+.... brief description of basic characteristics, reference to the appendix ....
+
+%------------------------------------------------------------------------------
 \section{OpReg-Boost}\label{sec:online-opreg}
 
-.... application of OpReg to online optimization ....
+Let now $\T_k : \R^n \to \R^n$ be a solver for the convex problem observed at time $t_k$, and assume that the operator has a term $\T_{f,k}$ depending exclusively on $f$ (\emph{e.g.} we have $\T_k = \T_k' \circ \T_{f,k}$).
+Since the sampled problem is convex, the solver $\T_k$ is non-expansive (actually, averaged, to guarantee convergence).
 
-% ------------------------------------------------------------------------------
+The idea then is to try and learn an approximation of $\T_k$ that is \emph{contractive} rather than non-expansive.
+
+Again, w.l.o.g. we are only interested in learning the term $\T_{f,k}$ that depends on $f$. The algorithm can be described as follows: at each time $t_k$ do:
+\begin{enumerate}
+	\item sample a new problem, that is, observe $f(\x; t_k)$ and $g(\x; t_k)$;
+
+	\item approximate the term $\T_{f,k}$ of the solver with a contractive one, and
+
+	\item apply the resulting solver. For example if $\T_k = \T_k' \circ \T_{f,k}$, then we apply $\T_k = \T_k' \circ \hat{\T}_{f,k}$ where $\hat{\T}_{f,k}$ is the learned operator.
+\end{enumerate}
+The learning step is performed using the (novel) constrained operator regression OpReg described in the following.
+
+In particular we have the following algorithm \nicola{make this pseudo code}
+For $\ell \in 0, 1, \ldots, M$ (for some $M \in \N$):
+\begin{itemize}
+	\item let $\x_k^\ell$ be the current approximate solution, we choose $D-1$ points around it, \emph{e.g.}
+	$$
+		\x_i = \x_k^\ell + \p_i, \ i = 2, \ldots, D, \ \p_i \sim \mathcal{N}(0, \sigma^2 \Im_n)
+	$$
+	and set $\x_1 = \x_k^\ell$;
+
+	\item we compute the data $\tv_i = \T_{f,k} \x_i$, $i = 1, \ldots, D$, for example $\tv_i = \x_i - \alpha \nabla f(\x_i; t_k)$;
+
+	\item we solve the OpReg, and use the approximate operator at $\x_k^\ell$, that is $\tv_1$, in the chosen solver $\T_k$:
+	$$
+		\x_k^{\ell+1} = \prox_{\alpha g}(\tv_1)
+	$$
+	where $\alpha$ is a step-size.
+\end{itemize}
+
+%------------------------------------------------
+\subsection{Interpolated version}
+
+%------------------------------------------------------------------------------
 \section{Numerical Results}\label{sec:numerical}
 
-.... simulation setup, reference to code (for now in supplementary materials), simulations ....
+%------------------------------------------------
+\subsection{Simulations set-up}
+We consider the following time-varying problem:
+\begin{equation}\label{eq:tv-problem}
+	\x^*(t_k) = \argmin_{\x \in \R^n} \frac{1}{2} \norm{\Am \x - \bv(t_k)}^2 + w \norm{\x}_1
+\end{equation}
+with $n = 10$, $\Am$ matrix with maximum and minimum (non-zero) eigenvalues $\sqrt{L} = 10^8$, $\sqrt{\mu} = 1$, and with rank $5$; $\y(t_k)$ has sinusoidal components with $3$ zero components.
+Due to $\Am$ being rank deficient, the cost $f$ is convex but not strongly so.
+
+%------------------------------------------------
+\subsection{Results}
 
@@
 
-\bibliography{main}
+\bibliography{references}
 \bibliographystyle{icml2021}
 
-%TODO: keep appendices in supplementary material only
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{}
+%------------------------------------------------------------------------------
+\section{PRS-Based QCQP solver}
+In this section we present a solver for OpReg which can be efficiently parallelized, inspired by the approach in \cite{simonetto_smooth_2021}.
+
+The idea is as follows: each pair of data points $i, j \in [D]$, $i \neq j$, gives rise to one constraint, for a total of $D(D-1)/2$ constraints. We define the following set of pairs
+$$
+	\mathcal{V} = \left\{ e = (i,j) \ | \ i, j \in [D], \ i < j \right\}
+$$
+which are ordered (that is, for example we take $(1,2)$ and not $(2,1)$, to avoid counting constraints twice).
+Clearly to each pair $e = (i,j)$ corresponds the constraint $\norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2$.
+
+Let now $\tv_{i,e}$ and $\tv_{j,e}$ be copies of $\tv_i$ and $\tv_j$ associated to the $e$-th constraint; then we can equivalently reformulate the OpReg~\eqref{eq:operator-regression} as
+\begin{subequations}\label{eq:equivalent-problem}
+\begin{align}
+	&\min_{\tv_{i,e}, \tv_{j,e}} \frac{1}{2 (D-1)} \sum_{e \in \mathcal{V}} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 \\
+	&\text{s.t.} \ \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \label{eq:interpolation-constraints} \\
+	&\qquad \tv_{i,e} = \tv_{i,e'} \ \forall e, e' | i \sim e, e'. \label{eq:consensus-constraints}
+\end{align}
+\end{subequations}
+Clearly~\eqref{eq:equivalent-problem} is a strongly convex problem with convex constraints defined in the variables $\tv_{i,e}$.
+
+%----------------------------------------
+\subsection{PRS solver}
+Let $\xx$ be the vector stacking all the $\tv_{i,e}$, then the problem is equivalent to
+\begin{align*}
+	\min_{\xx} f(\xx) + g(\xx)
+\end{align*}
+where
+$$
+	f(\xx) = \frac{1}{2(D-1)} \norm{\xx - \y}^2 + f_1(\xx)
+$$
+with $f_1$ the indicator function imposing~\eqref{eq:interpolation-constraints} and $g$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}.
+The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
+\begin{subequations}
+\begin{align}
+	&\xx^\ell = \prox_{\rho f}(\z^\ell) \label{eq:prs-xi} \\
+	&\vv^\ell = \prox_{\rho g}(2 \xx^\ell - \z^\ell) \\
+	&\z^{\ell+1} = \z^\ell + \vv^\ell - \xx^\ell.
+\end{align}
+\end{subequations}
+The proximal of $g$ corresponds to the projection onto the consensus space, and thus can be characterized simply by
+$$
+	\vv_{i,e}^\ell = \frac{1}{D-1} \sum_{e' | i \sim e'} \left( 2 \tv_{i,e'}^\ell - \z_{e'}^\ell\right).
+$$
+Regarding the proximal of $f$, is is clear that $f$ is separable, in the sense that it can be written as
+$$
+	f(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (D-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right]
+$$
+where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints}. Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
+\begin{equation}\label{eq:local-updates}
+\begin{split}
+	(\tv_{i,e},\tv_{j,e}) &= \argmin \left\{ \frac{1}{2 (D-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \frac{1}{2\rho} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \z_e^\ell} \right\}\\
+	&\text{s.t.} \quad \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2.
+\end{split}
+\end{equation}
+
+%------------------------------------------------------------
+\subsection{Local updates}
+The problems~\eqref{eq:local-updates} are quadratic programs with quadratic constraints, that is, they can be written in the form
+\begin{subequations}
+\begin{align}
+	&\min_{\xx} \frac{1}{2} \xx^\top \Pm_0 \xx + \langle \q_0, \xx \rangle \\
+	&\text{s.t.} \ \frac{1}{2} \xx^\top \Pm_1 \xx + \langle \q_1, \xx \rangle + r_1 \leq 0.
+\end{align}
+\end{subequations}
+In particular, for the cost function we have
+$$
+	\Pm_0 = \left( \frac{1}{D-1} + \frac{1}{\rho} \right) \Im_{2n}, \quad \q_0 = - \left( \frac{1}{D-1} \begin{bmatrix} \y_i \\ \y_j \end{bmatrix} + \frac{1}{\rho} \z_e^\ell \right)
+$$
+and for the constraint
+$$
+	\Pm_1 = 2 \begin{bmatrix} \Im_n & - \Im_n \\ - \Im_n & \Im_n \end{bmatrix}, \quad \q_1 = 0{2n}, \quad r_1 = - \zeta^2 \norm{\x_i - \x_j}^2.
+$$
+
+%------------------------------------------------------------------------------
+\section{Interpolation Using MAP}
 

### 2021-01-12 paper/main.tex
First commit/ start paper

@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\minimize}{minimize}
 \DeclareMathOperator{\prox}{prox}
@@
 \newcommand{\R}{\mathbb{R}}
-
+\newcommand{\f}{\mathbold{f}}
+\newcommand{\bdelta}{\mathbold{\delta}}
+\newcommand{\transp}{\top}
 \newcommand{\bv}{\mathbold{b}}
@@
 \begin{abstract}
-In this paper we propose a learning-based acceleration scheme for online optimization. .... novel operator regression ...
+We present OpReg-Boost, a novel acceleration scheme to boost the convergence properties and lessen the asymptotical error of online algorithms for time-varying (weakly) convex optimization problems.
+OpReg-Boost is built to learn the closest algorithm to a given online algorithm that has all the algorithmic properties one needs for fast convergence, and it is based on the concept of operator regression.
+We show how to build OpReg-Boost by using a Peaceman-Rachford solver, and further boost [...
+interpolation-MAP..].
+Simulation results showcase the [better/increase/..] properties of OpReg-Boost w.r.t.
+the more classical [...], and its close relative convex-regression-boost which is also novel but significantly less performing.
 \end{abstract}
@@
 
-.... problem formulation, literature review, contribution statement .....
+In recent years, we have witnessed the growing interest in time-varying optimization problems, where the cost function, constraints, or both are parametrized over data streams, and therefore are changing over time~\cite{a bunch}.
+Notable applications for the machine learning community are subspace tracking for video streaming and online sparse subspace clustering, see~\cite{1,2,3} and references therein.
+
+Solving time-varying optimization problems with online algorithms amounts to find and track continuously changing optimizers.
+If we let the optimizers trajectory be defined as $\x^*(t)$, a notable results for online algorithms in this context is that if the \emph{path-length} $\sum_{k=1}^T \|\x^*(t_{k+1}) - \x^*(t_{k})\|$, for subsequent time instances $t_{k+1}, t_k$, is not sub-linear in $T$, then online algorithms will have an asymptotical error $O(1)$~\cite{.,.} (or $O(T)$ in terms of pertinent notions of regret)\footnote{Jad..
+}.
+While errors can be made small, for instance with the use of prediction-correction algorithms~\cite{.,.}, the existence of an asymptotical error remains a distinctive feature of online algorithms for time-varying optimization.
+
+An eye-opening intuition is then to use the existence of said error to one's advantage, by introducing regularizations in the problem formulation that boost the algorithms convergence.
+In time-varying scenarios, where convergence rate is crucial, often time then one obtains smaller asymptotical error w.r.t.
+the original problem if one uses regularizations than if they do not.
+To reiterate, surprisingly, often \emph{there is no trade-off between accuracy and speed} and regularized problems offer better speed and asymptotical errors w.r.t.
+the original problem, even though we are modifying the problem formulation~\cite{.,.}.
+
+By building on this field-defining fact, once can ask what is the best regularization for a time-varying problem at hand?
+In this paper, we explore this question in two slightly different angles.
+First, we ask ourselves:
+
+{\bf (Q1) } \emph{what is the closest problem to a given time-varying problem that has all the functional properties we need for fast convergence?}
+
+This gives rise to convex-regression-based boosting.
+
+To fix the ideas, let us consider Figure.. where we have depicted a .. (as a bonus, since we define ..)
+
+\begin{figure}
+\centering
+\includegraphics[width=.925\columnwidth]{Figures/explanation}
+\caption{...}
+\label{fig.1}
+\end{figure}
+
+Convex regression is however not the only way to learn good problems, and not the best one (as we are going to explore in the simulation section).
+A better way is operator regression, which stems from the second question we ask:
+
+{\bf (Q2) } \emph{what is the closest algorithm to a given online algorithm for solving a time-varying problem that has all the algorithmic properties we need for fast convergence?  
+}
+
+Explain OpReg..
+
+In this paper, we offer the following contributions,
+\begin{enumerate}
+\item . 
+\end{enumerate}
+
+\subsection{Literature review}
+
+Time-varying optimization and online algorithms are widely treated in~\cite{.,.,.}, while a more machine learning approach is offered in~\cite{.} and subsequent work.
+The notion that regularizations help convergence possibly without introducing extra asymptotical error is presented in the papers~\cite{.,.,.}.
+While we refer to~\cite{1,2} for seminal papers close in spirit in the static domain.
+
+Learning the optimize and regularize is a growing research topic, and we cite~\cite{.,.}, as related work, even though not on the problem we are interested in solving here.
+
+Convex regression is treated extensively in~\cite{.,.,.}, while recently being generalized to smooth strongly convex functions~\cite{.} based on A. Taylor's work~\cite{.}.
+
+Operator regression is a recent and at the same old topic. We are going to build on the recent work~\cite{.} and the 19?? paper~\cite{.}.
+
+The acceleration schemes that we compare with are ..
+
+\subsection{Notation}
+
+Notation is wherever possible standard.
+We use the concept of $\mu$-weakly convex function, to indicate a function $f:\R^n \to \R$ that becomes convex by adding the term $\frac{\mu}{2} \|\x-\x_0\|^2_2$, $\mu >0$ (see~\cite{1,2,3}).
+The set of convex functions on $\R^n$ that are $L$-smooth (i.e., have $L$-Lipschitz continuous gradient) and $m$-strongly convex is indicated with $\mathcal{S}_{m,L}(\R^n)$.
+
+An operator $\T: \R^n \to \R^n$ is said to be non-expansive iff $\|T \x - T \y \| \leq \|\x- \y\|$, for all $\x, \y \in \R^n$, whereas it is $\zeta$-contractive, $\zeta\in(0,1)$, iff $\|T \x - T \y \| \leq \zeta \|\x- \y\|$, for all $\x, \y \in \R^n$.
+
+\section{Problem Formulation}
+
+We are interested in solving the following time-varying optimization problem,
+\begin{equation}\label{eq:continuous-time-problem}
+	\x^*(t) \in \argmin_{\x} f(\x; t) + g(\x; t)
+\end{equation}
+where $f : \R^n \times \R_+ \to \R$ is closed, proper, and $\mu$-weakly convex, whereas $g : \R^n \times \R_+ \to \R \cup \{ +\infty \}$ is closed, convex and proper function, optionally with $g \equiv 0$.
+Upon sampling the problem at discrete time instances $t_k$, we then obtain the sequence of time-invariant problems,
+\begin{equation}\label{eq:base-problem}
+	\x^*(t_k) \in \argmin_{\x} f(\x; t_k) + g(\x; t_k), \qquad k \in \N. 
+\end{equation}
+Our overarching goal is to set up an online algorithm $\mathcal{A}$ that generate a sequence of approximate optimizers $\{\x_k\}_{k\in \N}$, such that the asymptotical tracking error 
+\begin{equation}
+\limsup_{k \to \infty} \|\x_k - \x^*(t_k)\|,
+\end{equation}
+is as small as possible. Our main blanket assumption is that optimizers\footnote{..} at subsequent time instances cannot be arbitrarily far apart, that is, 
+\begin{equation}
+\|\x^*(t_{k+1}) - \x^*(t_k)\| \leq \Delta < +\infty, \qquad k \in \N,
+\end{equation}
+which in turn guarantees that the path-length grows linearly in time, 
+\begin{equation}
+\sum_{k\in \N} \|\x^*(t_{k+1}) - \x^*(t_k)\| \leq \Delta k.
+\end{equation}
+
+The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online algorithm $A$ (here a forward-backward algorithm) can obtain linear convergence to the asymptotical error bound $\Delta/(1-\gamma)$, with $\gamma = ..$; much weaker results hold for the general (weakly) convex case~\cite{.}.
+
+The second important result is that a Tikhonov regularization $..$..
+
+%% say something more, change?
+
+With this in place, our two main research questions are
+\begin{itemize}
+\item {\bf Q1.} Can we project the weakly convex function $f$ onto $\mathcal{S}_{m,L}(\R^n)$
+
+\item {\bf Q1.} Can we project the $A$ onto ??
+
+\end{itemize}
+
+\section{Q1. Convex Regression}
+
+We briefly introduce here the concept of convex regression, while we leave the main technical details to~\cite{1,2,3}.
+Suppose one has collected $\ell$ noisy measurements of a convex function $\varphi(\x): \R^n \to \R$ (say $y_i$) at points $\x_i \in \R^n$, $i \in I_{\ell}$.
+Then convex regression is a least-squares approach to estimate the generating function based on the measurements.
+Formally, letting $\varphi \in \mathcal{S}_{m,L}(\R^n)$, then one would like to solve the infinite-dimensional problem,
+\begin{equation}\label{eq.inf}
+\hat{\varphi}_{\ell} \in \argmin_{\psi \in \mathcal{S}_{m, L}(\R^n)}\Big\{ \sum_{i\in I_{\ell}} (y_i - \psi(\x_i))^2 \Big\} \,.
+\end{equation}
+
+The problem can be then equivalently decomposed into an estimation on the data points, to find the true function values and gradients at the data point ($\f = [\varphi_i]_{i \in I_{\ell}}$, $\bdelta = [\nabla \varphi_i]_{i \in I_{\ell}}$) which turns out to be a convex quadratically constrained quadratic program,
+\begin{subequations}\label{socp}
+\begin{eqnarray}
+\minimize_{\f\in\R^\ell\!,~ \bdelta \in\R^{n\ell}} && \sum_{i\in I_{\ell}} (y_i - \varphi_i)^2 \\
+\mathrm{subject~to:} &&
+\varphi_i - \varphi_j - \bdelta_j^\transp (\x_i - \x_j) \geq \\ && \quad \frac{1}{2(1 - m/L)}\left(\frac{1}{L}\|\bdelta_i - \bdelta_j \|^2_2 + m \|\x_i - \x_j\|_2^2 \right.
+\nonumber \\ && \quad \left.
+- 2 \frac{m}{L} (\bdelta_j-\bdelta_i)^\transp (\x_j - \x_i) \right), \quad \forall i, j \in I_n.
+\nonumber
+\end{eqnarray} 
+\end{subequations}
+
+And an interpolation scheme, that extends the point estimate over the whole space maintaining the functional properties, 
+\begin{equation}\label{interp}
+\hat{\varphi}_{\ell}(\x) = \mathrm{conv}(p_i(\x)) + \frac{m}{2} \|\x\|^2_2 \in \mathcal{S}_{m,L}(\R^n),
+\end{equation}
+where
+\begin{multline}
+p_i(\x) := \frac{L-m}{2} \| {\x} - \x_i\|_2^2 + (\bdelta_i^*-m \x_i)^\transp \x + \\ - \bdelta_i^{*,\transp} \x_i + f_i^* + m/2\|\x_i\|_2^2,
+\end{multline}
+and where $\mathrm{conv}(\cdot)$ indicates the convex hull.
+
+Then, to solve Q1, one could consider a number of evaluations of the function $f(\x; t_k)$ as noisy measurements of an underlying convex function $\varphi_k \in ..$ and using the least-squares approach above to \emph{project} function $f(\cdot; t_k)$ onto the space of ``good'' functions ..
+
+%% Complete.. put the details in the appendix..
 
 %------------------------------------------------------------------------------
-\section{Operator Regression}\label{sec:opreg}
+\section{Q2. Operator Regression}\label{sec:opreg}
+
+A slightly different approach to convex regression is to look at the algorithm directly, instead of the function.
+First of all, we remind the reader that any algorithm can be seen as an operator that maps the current approximate optimizer $\x_k$ into a new approximate optimizer $\x_{k+1}$.
+For example, a gradient algorithm of the form,
+\begin{equation}
+\x_{k+1} = \x_k - \alpha \nabla_{\x} f(\x_k; t_k) \equiv \underbrace{(I - \alpha \nabla_{x}f_k)}_{=:\T_k} (\x_k)
+\end{equation}
+where $\T_k: \R^n \to \R^n$ is the gradient algorithm operator.
+Interpreting algorithms as operators (possibly averaged, monotone, etc.) has been extremely fruitful for characterizing their convergence properties~\cite{,.,tom-also}.
+
+The counterpart of a smooth strongly convex function $\varphi_k$ in convex regression, is an operator that is contracting, i.e., ..
+In fact, while smooth strongly convex functions give rise to ...-contracting gradient algorithm operators, the space of contracting operators is larger (i.e., a function $f$ that ..
+could give rise to ..).
+
+The key idea now is to interpret .. as measurement of a true .. operator that we want to estimate.
+
+% GENERAL PROBLEM..
+
+% FIrst, on the data points
+
+First of all, we define the observations
+$$
+	\y_i = \T_f \x_i + \e_i, \quad i \in [D]
+$$
+of the operator we want to regularize. Now, using Fact~2.2 in \cite{ryu_operator_2020} we know that an operator $\T$ is $\zeta$-contractive interpolable if and only if it satisfies
+$$
+	\norm{\T \x_i - \T \x_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2, \quad \forall i,j \in [D], \ i \neq j.
+$$
+Therefore, we can define the following constrained regression problem:
+\begin{equation}\label{eq:operator-regression}
+\begin{split}
+	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \ \forall i,j \in [D], i \neq j
+\end{split}
+\end{equation}
+where again the cost function is a least square terms on the observations and the constraints enforce contractiveness.
+
+%% Then Interpolation here..
+
+\subsection{Auto-tuning }
+
+\subsection{PRS-based solver}
+
+\section{OpReg-Boost}
+
+..
+
+To iron this..
 
@@
 
+%% PUT THIS SOMEWHERE
 Problem~\eqref{eq:base-problem} is convex but not strongly so, which means that the performance of online algorithms applied to it is worse than the performance attainable for strongly convex problems.
@@
 %------------------------------------------------
-\subsection{Operator regression}
+\subsection{Q2. Operator regression}
 First of all, we define the observations

### 2021-01-12 paper/motivating_results.tex

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,tikz}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{bm,fixmath}
\usepackage{color}
\usepackage{subcaption}
\usepackage{xspace}

\usetikzlibrary{calc,shapes,arrows.meta,decorations.pathreplacing,decorations.markings}

% math operators
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\prox}{prox}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\fix}{fix}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\image}{Im}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\udist}{\overline{dist}}
\DeclareMathOperator{\ldist}{\underline{dist}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
% double inner product
\newcommand{\zprod}[1]{\langle\kern-0.25ex\langle#1\rangle\kern-0.25ex\rangle}
% triple norm
\newcommand{\znorm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}

% theorem environments
\usepackage{amsthm}

\theoremstyle{plain} % Plain: italic text, extra space above and below
\newtheorem{example}{Example}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{axiom}[theorem]{Axiom}

\theoremstyle{definition} % Definition: upright text, extra space above and below
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{remark} % Remark: upright text, no extra space above or below
\newtheorem{remark}[theorem]{Remark}

% algorithms packages and commands
\usepackage{algorithm}
\usepackage{algpseudocode}

% define commands for algorithm environment
\algrenewcommand\algorithmicrequire{\textbf{Input:}}

% new math commands
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}

\newcommand{\x}{\mathbold{x}}
\newcommand{\y}{\mathbold{y}}

\newcommand{\I}{\mathcal{I}}
\newcommand{\T}{\mathcal{T}}

% file's info
\author{Nicola Bastianello}
\title{Motivating Results}

\begin{document}

\maketitle

%---------------------------------------------------------------------------
\section{Result 1 (static)}
The following result shows that the fixed point residual converges linearly fast for contractive operators, but sub-linearly (with the square root of the iteration number) for averaged operators.

\begin{proposition}
Consider an operator $\T : \R^n \to \R^n$ and the Banach-Picard iteration
$$
	\x^{\ell+1} = \T \x^\ell, \quad \ell \in \N.
$$
Then, the fixed point residual $\{ \norm{\x^{\ell+1} - \x^\ell} \}$ is bounded as:
\begin{itemize}
	\item \emph{$\T$ $\zeta$-contractive}: $\norm{\x^{\ell+1} - \x^\ell} \leq (1 + \zeta) \zeta^\ell \norm{\x^0 - \x^*}$;

	\item \emph{$\T$ $\alpha$-averaged}: $\norm{\x^{\ell+1} - \x^\ell} \leq \frac{1}{\sqrt{\ell+1}} \sqrt{\frac{\alpha}{1 - \alpha}} \norm{\x^0 - \x^*}$.
\end{itemize}
\end{proposition}
%
\begin{proof}
\emph{$\T$ contractive}: by \cite[Theorem~1.50]{bauschke_convex_2017} we know that
$$
	\norm{\x^\ell - \x^*} \leq \zeta^\ell \norm{\x^0 - \x^*};
$$
using the triangle inequality we then have
\begin{align*}
	\norm{\x^{\ell+1} - \x^\ell} &\leq \norm{\x^{\ell+1} - \x^*} + \norm{\x^\ell - \x^*} \\
	&\leq \zeta \norm{\x^\ell - \x^*} + \norm{\x^\ell - \x^*} \\
	&\leq (1 + \zeta) \norm{\x^\ell - \x^*} \\
	&\leq (1 + \zeta) \zeta^\ell \norm{\x^0 - \x^*}.
\end{align*}

\emph{$\T$ averaged}: by the averagedness of $\T$ we can write, for some $\x^* \in \fix(\T)$:
$$
	\norm{\x^{\ell+1} - \x^*}^2 \leq \norm{\x^\ell - \x^*}^2 - \frac{1 - \alpha}{\alpha} \norm{\x^{\ell+1} - \x^\ell}^2;
$$
rearranging, and summing over time we get
$$
	\sum_{h = 0}^\ell \norm{\x^{h+1} - \x^h}^2 \leq \frac{\alpha}{1 - \alpha} \norm{\x^0 - \x^*}^2
$$
where we used the telescoping sum and removed the negative term $- \norm{\x^{\ell+1} - \x^\ell}^2$.

Since $\{ \norm{\x^{h+1} - \x^h}^2 \}$ is a monotonically decreasing sequence, we know that $(\ell+1) \norm{\x^{\ell+1} - \x^h} \leq \sum_{h = 0}^\ell \norm{\x^{h+1} - \x^h}^2$; using this fact, rerranging and taking the square root yields the thesis.
\end{proof}

%---------------------------------------------------------------------------
\section{Result 2 (dynamic)}
Consider the time-varying Banach-Picard
$$
	\x_{k+1} = \T_{k+1} \x_k, \quad k \in \N,
$$
and for simplicity assume that $\x_0 \in \fix(\T_0)$.

\begin{proposition}
The cumulative fixed point residual is bounded as:
\begin{itemize}
	\item \emph{$\T_k$ $\zeta$-contractive}:
	$$
		\frac{1}{k+1} \sum_{h = 0}^k \norm{\x_{h+1} - \x_h}^2 \leq \left( \sigma \frac{1 + \zeta}{1 - \zeta} \right)
	$$
	where $\sigma \geq \max_k \norm{\x_k^* - \x_{k-1}^*}$;

	\item \emph{$\T_k$ $\alpha$-averaged} and defined on a compact domain:
	$$
		\frac{1}{k+1} \sum_{h = 0}^k \norm{\x_{h+1} - \x_h}^2 \leq \frac{\alpha}{1 - \alpha} (\tau^2 + 2 \delta \tau)
	$$
	where $\tau$ is the maximum distance between consecutive fixed point sets $\fix(\T_k)$ and $\fix(\T_{k-1})$, and $\delta$ is the diameter of $\T_k$'s domains.
\end{itemize}
\end{proposition}
%
\begin{proof}
\emph{$\T_k$ contractive}: using triangle inequality and contractiveness we can write
\begin{align*}
	\norm{\x_{k+1} - \x_k} &\leq \norm{\x_{k+1} - \x_{k+1}^*} + \norm{\x_k - \x_{k+1}^*} \\
	&\leq (1 + \zeta) \norm{\x_k - \x_{k+1}^*} \\
	&\leq (1 + \zeta) (\norm{\x_k - \x_k^*} + \sigma) \\
	&\leq (1 + \zeta) \left( \zeta^k \norm{\x_0 - \x_0^*} + \frac{\sigma}{1 - \zeta} \right) = \frac{1 + \zeta}{1 - \zeta} \sigma.
\end{align*}

Taking the square and averaging over time we get:
\begin{align*}
	\frac{1}{k+1} \sum_{h = 0}^k \norm{\x_{h+1} - \x_h}^2 \leq \left( \frac{1 + \zeta}{1 - \zeta} \sigma \right)^2.
\end{align*}

\emph{$\T_k$ averaged}: using the averagedness we have
$$
	\norm{\x_{k+1} - \x_{k+1}^*}^2 \leq \norm{\x_k - \x_{k+1}^*}^2 - \frac{1 - \alpha}{\alpha} \norm{\x_{k+1} - \x_k}^2;
$$
rearranging and using triangle and Cauchy-Schwarz inequalities we have
\begin{align*}
	\norm{\x_{k+1} - \x_k}^2 &\leq \frac{\alpha}{1 - \alpha} \left( \norm{\x_k -\x_{k+1}^*}^2 - \norm{\x_{k+1} - \x_{k+1}^*}^2 \right) \\
	&\leq \frac{\alpha}{1 - \alpha} \left( \norm{\x_k - \x_k^*}^2 - \norm{\x_{k+1} - \x_{k+1}^*}^2 + \norm{\x_k^* - \x_{k+1}^*}^2 + 2 \norm{\x_k - \x_{k+1}^*} \norm{\x_k^* - \x_{k+1}^*} \right) \\
	&\leq \frac{\alpha}{1 - \alpha} \left( \norm{\x_k - \x_k^*}^2 - \norm{\x_{k+1} - \x_{k+1}^*}^2 + \tau^2 + 2 \delta \tau \right)
\end{align*}
where the last inequality follows by $\norm{\x_k^* - \x_{k-1}^*} \leq \tau$ and $\delta$ being the diameter of the compact domain.

Averaging over time, and noticing that the error terms cancel out we have
$$
	\frac{1}{k+1} \sum_{h = 0}^k \norm{\x_{h+1} - \x_h}^2 \leq \frac{\alpha}{1 - \alpha} \left( \frac{1}{k+1} \norm{\x_0 - \x_0^*}^2 + \tau^2 + 2 \delta \tau \right) = \frac{\alpha}{1 - \alpha} (\tau^2 + 2 \delta \tau).
$$
\end{proof}

\bibliographystyle{ieeetr}
\bibliography{references}

\end{document}

### 2021-01-13 reg4opt/utils.py
added convex regression

@@ -16,14 +16,14 @@ ran = default_rng()
 from tvopt import sets
 
 
-#%% DATA GENERATION FOR OPERATOR REGRESSION
+#%% DATA GENERATION FOR REGRESSION METHODS
 
-def generate_data(T, x, num_data, method="normal", **kwargs):
+def sample_training_points(x, num_data, method="normal", **kwargs):
     """
-    Generate the training data for an operator regression problem.
+    Sample training points.
     
-    The function encapsulates different method of generating the training data
-    for an operator regression problem. The choices are
+    The function encapsulates different methods of generating the training 
+    points for a regression problem. The choices are
     
     * normal: the data are chosen as :math:`x + d_i`, where
       :math:`d_i` are random vectors with normal distribution;
@@ -32,6 +32,47 @@ def generate_data(T, x, num_data, method="normal", **kwargs):
       :math:`e_j` a randomly selected vector of the standard basis;
     * uniform: the data are chosen as :math:`x + d_i`, where
       :math:`d_i` are random vectors with uniform distribution.
+
+    Parameters
+    ----------
+    x : ndarray
+        The center of the training data, that is, all other training points are
+        chosen as perturbations of `x`.
+    num_data : int
+        The number of training points, including `x`, which means that 
+        `num_data`-1 points are randomly selected.
+    method : str, optional
+        The method to choose the training points, defaults to "normal". 
+        Alternatives are "fireworks" (alias "fw", "f") and "uniform" (alias "u").
+    **kwargs : tuple
+        The arguments of `method`.
+
+    Returns
+    -------
+    list
+        The points :math:`x_i` selected by the method.
+    """
+    
+    if method == "fireworks" or method == "fw" or method == "f":
+        # pick directions and magnitudes
+        d = ran.choice(range(x.size), size=num_data-1, replace=False)
+        m = math.sqrt(kwargs["var"])*ran.standard_normal(num_data-1)
+        
+        # create the points
+        return [x] + [x + m[i]*_standard_basis(d[i], x.size) for i in range(num_data-1)]
+    
+    elif method == "uniform" or method == "u":
+        return [x] + [x + 2*kwargs["a"]*ran.random(x.shape)-kwargs["a"] for _ in range(num_data-1)]
+        
+    else: # normal
+        return [x] + [x + math.sqrt(kwargs["var"])*ran.standard_normal(x.shape) for _ in range(num_data-1)]
+
[…]

### 2021-01-13 examples/online_linear_regression.py
updated example

@@ -18,9 +18,9 @@ from tvopt.utils import random_matrix
 from tvopt import costs, solvers
 
 from reg4opt.operators import Gradient, Proximal
-from reg4opt.regression import operator_regression
+from reg4opt.regression import operator_regression, convex_regression
 from reg4opt.interpolation import interpolator
-from reg4opt.utils import print_progress, generate_data
+from reg4opt.utils import print_progress, generate_data, generate_data_cr
 from reg4opt.solvers import fista, anderson_acceleration
 
 
@@ -82,6 +82,7 @@ num_data = 5
 var = 1e-2 # for choosing training data
 
 bar_zeta = 0.5 # contraction constant of approximate operator
+bar_mu, bar_L = 1, 1e5 # strong convexity and smoothness moduli
 
 num_iter = 5 # num. of iterations per sampled problem
 
@@ -106,7 +107,6 @@ print("Proximal gradient method ...")
 x = np.zeros(f.dom.shape + (f.time.num_samples+1,))
 x[...,0] = x0
 
-t = 0
 
 for k in range(f.time.num_samples):
     
@@ -127,7 +127,6 @@ print("FISTA ...")
 x = np.zeros(f.dom.shape + (f.time.num_samples+1,))
 x[...,0] = x0
 
-t = 0
 
 for k in range(f.time.num_samples):
     
@@ -149,7 +148,6 @@ x = np.zeros(f.dom.shape + (f.time.num_samples+1,))
 x[...,0] = x0
 x_old = [x0]
 
-t = 0
 
 for k in range(f.time.num_samples):
     
@@ -175,13 +173,12 @@ for k in range(f.time.num_samples):
 err_aa = [la.norm(x[...,k+1] - s[:,[k]]) for k in range(f.time.num_samples)]
 
 
-# -------------------- PRS
-print("OpReg (PRS) ...")
+# -------------------- OPERATOR REGRESSION
+print("OpReg ...")
 
 x = np.zeros(f.dom.shape + (f.time.num_samples+1,))
 x[...,0] = x0
 
-t = 0
 
 for k in range(f.time.num_samples):
     
@@ -193,7 +190,7 @@ for k in range(f.time.num_samples):
     for _ in range(num_iter):
         
         # generate training data
-        x_i, y_i = generate_data(T_k, y, num_data, var)
+        x_i, y_i = generate_data(T_k, y, num_data, var=var)
         
[…]

### 2021-01-13 paper/main.tex
second day on the paper

@@
 
-In recent years, we have witnessed the growing interest in time-varying optimization problems, where the cost function, constraints, or both are parametrized over data streams, and therefore are changing over time~\cite{a bunch}.
-Notable applications for the machine learning community are subspace tracking for video streaming and online sparse subspace clustering, see~\cite{1,2,3} and references therein.
+[Add others' papers, esp. ML community]
+
+In recent years, we have witnessed the growing interest in time-varying optimization problems, where the cost function, constraints, or both are parametrized over data streams, and therefore are changing over time~\cite{Jadbabaie2015, SPM}.
+Notable applications for the machine learning community are subspace tracking for video streaming and online sparse subspace clustering, see~\cite{Asif2014, Akhriev2020, SPM} and references therein.
 
 Solving time-varying optimization problems with online algorithms amounts to find and track continuously changing optimizers.
-If we let the optimizers trajectory be defined as $\x^*(t)$, a notable results for online algorithms in this context is that if the \emph{path-length} $\sum_{k=1}^T \|\x^*(t_{k+1}) - \x^*(t_{k})\|$, for subsequent time instances $t_{k+1}, t_k$, is not sub-linear in $T$, then online algorithms will have an asymptotical error $O(1)$~\cite{.,.} (or $O(T)$ in terms of pertinent notions of regret)\footnote{Jad..
+If we let the optimizers trajectory be defined as $\x^*(t)$, a significant results for online algorithms in this context is that if the \emph{path-length} $\sum_{k=1}^T \|\x^*(t_{k+1}) - \x^*(t_{k})\|$, for subsequent time instances $t_{k+1}, t_k$, is not sub-linear in $T$, then online algorithms will have an asymptotical error $O(1)$~\cite{Besbes2013, Jadbabaie2015, SPM, NaLi2020} (or $O(T)$ in terms of pertinent notions of regret)\footnote{
+%%% Footnote Jadbabaie:
+In~\cite{Jadbabaie2015} and subsequent works, [Finish]
+%%%
 }.
-While errors can be made small, for instance with the use of prediction-correction algorithms~\cite{.,.}, the existence of an asymptotical error remains a distinctive feature of online algorithms for time-varying optimization.
+While errors can be made small, for instance with the use of prediction-correction algorithms~\cite{Dontchev2013, simonetto_time-varying_2020}, the existence of an asymptotical error remains a distinctive feature of online algorithms for time-varying optimization.
 
@@
 the original problem if one uses regularizations than if they do not.
-To reiterate, surprisingly, often \emph{there is no trade-off between accuracy and speed} and regularized problems offer better speed and asymptotical errors w.r.t.
-the original problem, even though we are modifying the problem formulation~\cite{.,.}.
+To reiterate, surprisingly, often when one uses pertinent regularizations, \emph{there is no trade-off between accuracy and speed} and regularized problems offer better speed and asymptotical errors w.r.t.
+the original problem, even though we are modifying the problem formulation~\cite{Simonetto2014d, Bastianello2020asi}.
 
@@
 
-To fix the ideas, let us consider Figure.. where we have depicted a .. (as a bonus, since we define ..)
-
-\begin{figure}
-\centering
-\includegraphics[width=.925\columnwidth]{Figures/explanation}
-\caption{...}
-\label{fig.1}
-\end{figure}
+To fix the ideas in a static setting, let us consider Figure~\ref{fig.1}, where we have depicted a non-convex function $f$, which we can evaluate at specific points (grey dot).
+The idea behind Q1 and convex-regression-based boosting is then to interpret the functional evaluation as noisy measurements of an underlying true convex function $\hat{f}$, which we want to learn.
+As long as $f$ and $\hat{f}$ are not dramatically different, the reasoning is that solving the problem of minimizing $\hat{f}$ instead of $f$ will then give us a boost in term of convergence rate and asymptotical error in online algorithm, despite the fact that $f$ and $\hat{f}$ are different.
+In addition, and for free, since we have some liberty in designing the functional properties of $\hat{f}$ (e.g., Lipschitz constant, strong convexity constant, etc.), we can thoroughly optimize the parameter of the online algorithm, e.g., its stepsize, further boosting convergence.
 
@@
 
-Explain OpReg..
+In Figure~\ref{fig.1}, we have reported the case of a gradient descent algorithm in terms of a fixed point operator $\mathcal{T} = I - \alpha \nabla_{x}f$, with $\alpha>0$ being the stepsize.
+The idea here is to use evaluations of $\mathcal{T}$ as noisy measurements of a true underlying operator $\hat{\mathcal{T}}$, with useful properties (e.g., a contractive operator).
+By using $\hat{\mathcal{T}}$ en lieu of $\mathcal{T}$, then one will be able to boost convergence and reduce the asymptotical error, once again, if $\mathcal{T}$ and $\hat{\mathcal{T}}$ are not dramatically different.
+
+This latter methodology offers the most promise (as we will showcase in simulation) and it is what we call OpReg-Boost (boosting by operator regression).
+
+\begin{figure}
+\centering
+\includegraphics[width=.925\columnwidth]{Figures/explanation}
+\caption{The idea of boosting via projection onto the space of ``good'' functions or ``good'' fixed point operators.
+One can interpret the evaluation of function $f$ or operator $\mathcal{T}$ as noisy evaluations of an underlying ``better'' function or operator, $\hat{f}$ and $\hat{\mathcal{T}}$, respectively, and use the latter to solve the problem instead.
+This gives rise to convex-regression-based boosting or operation-regression-based boosting (OpReg-Boost).}
+\label{fig.1}
+\end{figure}
 
@@
 \begin{enumerate}
-\item . 
+\item We present two novel regression methods to \emph{learn-project-and-solve} time-varying optimization problems that are not necessarily convex.
+The methods are based on convex regression and operator regression, and -- especially the latter -- is promising in boosting convergence without introducing a larger asymptotical error.
+%%
+\item We present efficient ways to solve the operation regression problem via a pertinent reformulation of the Peaceman-Rachford splitting method. [.. more ]
+%%
+\item We [Interpolation]
+%%
+\item We showcase the [simulation results]
 \end{enumerate}
@@
 
-Time-varying optimization and online algorithms are widely treated in~\cite{.,.,.}, while a more machine learning approach is offered in~\cite{.} and subsequent work.
-The notion that regularizations help convergence possibly without introducing extra asymptotical error is presented in the papers~\cite{.,.,.}.
-While we refer to~\cite{1,2} for seminal papers close in spirit in the static domain.
+Time-varying optimization and online algorithms are extensively covered in~\cite{SPM, simonetto_time-varying_2020} and references therein, while a more machine learning approach is offered in~\cite{Jadbabaie2015} and subsequent work.
+The notion that regularizations help convergence possibly without introducing extra asymptotical error is presented in the papers~\cite{Simonetto2014d, Bastianello2020asi}.
+While we refer to~\cite{Devolder2011,Nedic2011} for seminal papers close in spirit in the static domain.
 
-Learning the optimize and regularize is a growing research topic, and we cite~\cite{.,.}, as related work, even though not on the problem we are interested in solving here.
+Learning the optimize and regularize is a growing research topic, and we cite~\cite{Nghiem2018,Ongie2020}, as related work, even though not on the problem we are interested in solving here.
 
-Convex regression is treated extensively in~\cite{.,.,.}, while recently being generalized to smooth strongly convex functions~\cite{.} based on A. Taylor's work~\cite{.}.
+Convex regression is treated extensively in~\cite{Seijo2011,Lim2012,Mazumder2019,Blanchet2019}, while recently being generalized to smooth strongly convex functions~\cite{simonetto_smooth_2021} based on A.
+Taylor's works~\cite{Taylor2016, Taylor2017}.
 
-Operator regression is a recent and at the same old topic. We are going to build on the recent work~\cite{.} and the 19?? paper~\cite{.}.
+Operator regression is a recent and at the same time old topic. We are going to build on the recent work~\cite{ryu_operator_2020} and the F.A. Valentine's 1945 paper~\cite{valentine_lipschitz_1945}.
 
-The acceleration schemes that we compare with are ..
+The acceleration schemes that we compare with are [Tell and cite] e.g., AA: \cite{pmlr-v119-mai20a}
 
@@
 Notation is wherever possible standard.
-We use the concept of $\mu$-weakly convex function, to indicate a function $f:\R^n \to \R$ that becomes convex by adding the term $\frac{\mu}{2} \|\x-\x_0\|^2_2$, $\mu >0$ (see~\cite{1,2,3}).
+We use the concept of $\mu$-weakly convex function, to indicate a function $f:\R^n \to \R$ that becomes convex by adding the term $\frac{\mu}{2} \|\x-\x_0\|^2_2$, $\mu >0$ (see~\cite{Duchi2018,Davis2019,pmlr-v119-mai20b}).
 The set of convex functions on $\R^n$ that are $L$-smooth (i.e., have $L$-Lipschitz continuous gradient) and $m$-strongly convex is indicated with $\mathcal{S}_{m,L}(\R^n)$.
@@
 An operator $\T: \R^n \to \R^n$ is said to be non-expansive iff $\|T \x - T \y \| \leq \|\x- \y\|$, for all $\x, \y \in \R^n$, whereas it is $\zeta$-contractive, $\zeta\in(0,1)$, iff $\|T \x - T \y \| \leq \zeta \|\x- \y\|$, for all $\x, \y \in \R^n$.
+
+The prox operator [..]
 
@@
 
-The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online algorithm $A$ (here a forward-backward algorithm) can obtain linear convergence to the asymptotical error bound $\Delta/(1-\gamma)$, with $\gamma = ..$; much weaker results hold for the general (weakly) convex case~\cite{.}.
+The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online algorithm $A$ (here a forward-backward algorithm) can obtain linear convergence to the asymptotical error bound $\Delta/(1-\gamma)$, with optimal $\gamma = \frac{L-m}{L+m}$; much weaker results hold for the general convex case~\cite{Simonetto20XX}, for example [..]
 
-The second important result is that a Tikhonov regularization $..$..
+The second important result is that even a simple Tikhonov regularization $+ \frac{w}{2} \|x\|^2_2$, transforming a smooth but not strongly convex case into a strongly convex one allows for a boost in convergence and [..]
 
@@
 \begin{itemize}
-\item {\bf Q1.} Can we project the weakly convex function $f$ onto $\mathcal{S}_{m,L}(\R^n)$
+\item {\bf Q1.} Can we project the weakly convex function $f$ onto $\mathcal{S}_{m,L}(\R^n)$ and learn a better function $\hat{f}$ that has all the functional properties we need (e.g., smooth strong convexity) and use that to solve the problem instead?
 
-\item {\bf Q1.} Can we project the $A$ onto ??
+\item {\bf Q2.} Can we project the fixed point operator of the algorithm we use $\mathcal{T}$ onto the set of contracting operators, learn a better operator $\hat{\mathcal{T}}$, and use that to solve the problem instead?
 
@@
 
-We briefly introduce here the concept of convex regression, while we leave the main technical details to~\cite{1,2,3}.
+We briefly introduce here the concept of convex regression, while we leave the main technical details to~\cite{Mazumder2019,simonetto_smooth_2021}.
 Suppose one has collected $\ell$ noisy measurements of a convex function $\varphi(\x): \R^n \to \R$ (say $y_i$) at points $\x_i \in \R^n$, $i \in I_{\ell}$.
@@
 \begin{eqnarray}
-\minimize_{\f\in\R^\ell\!,~ \bdelta \in\R^{n\ell}} && \sum_{i\in I_{\ell}} (y_i - \varphi_i)^2 \\
-\mathrm{subject~to:} &&
-\varphi_i - \varphi_j - \bdelta_j^\transp (\x_i - \x_j) \geq \\ && \quad \frac{1}{2(1 - m/L)}\left(\frac{1}{L}\|\bdelta_i - \bdelta_j \|^2_2 + m \|\x_i - \x_j\|_2^2 \right.
-\nonumber \\ && \quad \left.
-- 2 \frac{m}{L} (\bdelta_j-\bdelta_i)^\transp (\x_j - \x_i) \right), \quad \forall i, j \in I_n.
+(\f^*, \bdelta^*) &&= \argmin_{\f\in\R^\ell\!,~ \bdelta \in\R^{n\ell}} \sum_{i\in I_{\ell}} (y_i - \varphi_i)^2 \\
+\mathrm{s.t.:} &&
+\varphi_i - \varphi_j - \bdelta_j^\transp (\x_i - \x_j) \geq \\ && \hskip-5mm \frac{1}{2(1 - m/L)}\left(\frac{1}{L}\|\bdelta_i - \bdelta_j \|^2_2 + m \|\x_i - \x_j\|_2^2 \right.
+\nonumber \\ && \hskip-5mm \left.
+- 2 \frac{m}{L} (\bdelta_j-\bdelta_i)^\transp (\x_j - \x_i) \right), \quad \forall i, j \in I_{\ell}.
 \nonumber
@@
 
-Then, to solve Q1, one could consider a number of evaluations of the function $f(\x; t_k)$ as noisy measurements of an underlying convex function $\varphi_k \in ..$ and using the least-squares approach above to \emph{project} function $f(\cdot; t_k)$ onto the space of ``good'' functions ..
-
-%% Complete.. put the details in the appendix..
+Then, to solve Q1, one could consider a number of evaluations of the function $f(\x; t_k)$ as noisy measurements of an underlying convex function $\varphi_k \in \mathcal{S}_{m,L}(\R^n)$ and using the least-squares approach above to \emph{project} function $f(\cdot; t_k)$ onto the space of ``good'' functions [Complete..
+put the details in the appendix]
 
@@
 where $\T_k: \R^n \to \R^n$ is the gradient algorithm operator.
-Interpreting algorithms as operators (possibly averaged, monotone, etc.) has been extremely fruitful for characterizing their convergence properties~\cite{,.,tom-also}.
+Interpreting algorithms as operators (possibly averaged, monotone, etc.) has been extremely fruitful for characterizing their convergence properties~\cite{Rockafellar1976, Eckstein1989, bauschke_convex_2017,Ryu2015,tom-also}.
 
-The counterpart of a smooth strongly convex function $\varphi_k$ in convex regression, is an operator that is contracting, i.e., ..
-In fact, while smooth strongly convex functions give rise to ...-contracting gradient algorithm operators, the space of contracting operators is larger (i.e., a function $f$ that ..
-could give rise to ..).
+The counterpart of a smooth strongly convex function $\varphi_k$ in convex regression, is an operator that is contracting, i.e., $\|\T_k \x - \T_k \y\| \leq \zeta \|\x - \y\|$ for all $\x, \y \in \R^n$ and $\zeta \in (0,1)$.
+In fact, while $L$-smooth $m$-strongly convex functions give rise to gradient operators that are $..$-contracting, the space of contracting operators is larger (i.e., a function $f$ that is not strongly convex could in principle give rise to a contracting operator~\cite{linear}).
 
-The key idea now is to interpret .. as measurement of a true .. operator that we want to estimate.
+The key idea now is to interpret evaluations of $\T_k$ as measurements of a true underlying contracting operator that we want to estimate.
 
 % GENERAL PROBLEM.. 
+% First, on the data points
 
-% FIrst, on the data points
-
-First of all, we define the observations
-$$
-	\y_i = \T_f \x_i + \e_i, \quad i \in [D]
-$$
-of the operator we want to regularize. Now, using Fact~2.2 in \cite{ryu_operator_2020} we know that an operator $\T$ is $\zeta$-contractive interpolable if and only if it satisfies
-$$
-	\norm{\T \x_i - \T \x_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2, \quad \forall i,j \in [D], \ i \neq j.
-$$
-Therefore, we can define the following constrained regression problem:
+First of all, using Fact~2.2 in \cite{ryu_operator_2020}, we know that an operator $\T$ is $\zeta$-contractive interpolable (and therefore extensible to the whole space) if and only if it satisfies
+\begin{equation}
+	\norm{\T \x_i - \T \x_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2, \quad \forall i,j \in I_{\ell}, \ i \neq j.
+\end{equation}
+Therefore, we can define the following convex quadratically constrained quadratic program as our regression problem:
 \begin{equation}\label{eq:operator-regression}
 \begin{split}
-	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 \\
-	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \ \forall i,j \in [D], i \neq j
+	\hat{\tv} &= \argmin_{ \R^{n\ell} \ni \tv = [\tv_i]_{i \in I_{\ell}}} \frac{1}{2} \sum_{i \in I_{\ell}} \norm{\tv_i - \T_k \x_i}^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \ \forall i,j \in I_{\ell}, i \neq j,
 \end{split}
 \end{equation}
-where again the cost function is a least square terms on the observations and the constraints enforce contractiveness.
+where again the cost function is a least square terms on the ``observations''' and the constraints enforce contractiveness.
+In particular, the optimal values $\hat{\tv}$ on the data points represent the evaluations of a $\zeta$-contracting operator when applied to those points.
+
+To extend [interpolation here]
 
@@
 
-\subsection{Auto-tuning }
+\subsection{Optional auto-tuning }
+
+Discretionarily, we can also modify~\eqref{eq:operator-regression} by including $w = \zeta^2$ as an unknown of the regression problem with a penalty $c>0$, which then becomes
+\begin{equation}
+\begin{split}
+	(\hat{\tv}, \hat{w}) &= \argmin_{ \R^{n\ell} \ni \tv = [\tv_i]_{i \in I_{\ell}}, w \in (0,1)} \frac{1}{2} \sum_{i \in I_{\ell}} \norm{\tv_i - \y_i}^2 + \frac{c}{2} w^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 - w \norm{\x_i - \x_j}^2 \leq 0 \ \forall i,j \in I_{\ell}, i \neq j,
+\end{split}
+\end{equation}
+this way the contraction constant does not need to be specified, and it is \emph{auto-tuned} by the regression.
 
@@
 
-\section{OpReg-Boost}
-
-..
-
-To iron this..
-
-%------------------------------------------------
-\subsection{Problem formulation}
-Consider the following \emph{convex, time-varying} optimization problem
-\begin{equation}\label{eq:continuous-time-problem}
-	\x^*(t) \in \argmin f(\x; t) + g(\x; t)
-\end{equation}
-where $f : \R^n \times \R_+ \to \R$ and $g : \R^n \times \R_+ \to \R \cup \{ +\infty \}$ are closed, convex and proper functions, optionally with $g \equiv 0$.
-In particular, we are interested in solving the following sequence of static problems derived from sampling~\eqref{eq:continuous-time-problem} at the times $\{ t_k \}_{k \in \N}$, $t_{k+1} - t_k = \Ts$:
-\begin{equation}\label{eq:base-problem}
-	\x^*(t) \in \argmin f(\x; t_k) + g(\x; t_k).
-\end{equation}
-
-%% PUT THIS SOMEWHERE
-Problem~\eqref{eq:base-problem} is convex but not strongly so, which means that the performance of online algorithms applied to it is worse than the performance attainable for strongly convex problems.
-As an example, consider the case $g \equiv 0$, and apply an online gradient descent: if the problem is convex the (static) regret is $O(\sqrt{T})$, with $T$ the number of sampling times, while if the problem is strongly convex the regret is $O(\log(T))$, section~3.1 in \cite{hazan_introduction_2016}.
-\nicola{Instead of citing Hazan, we should derive a result in an appendix, for example for the fixed point residual}
-
-As we can see from the results just mentioned, in general in online optimization it is not possible to achieve zero regret, due to the dynamic nature of the problem.
-However, for strongly convex problems smaller regrets can be achieved.
-
-The goal then is to design learning techniques that allow to achieve strongly convex-like performance while tracking a solution trajectory of the problem~\eqref{eq:base-problem} with good accuracy.
-
-%------------------------------------------------
-\subsection{Q2. Operator regression}
-First of all, we define the observations
-$$
-	\y_i = \T_f \x_i + \e_i, \quad i \in [D]
-$$
-of the operator we want to regularize. Now, using Fact~2.2 in \cite{ryu_operator_2020} we know that an operator $\T$ is $\zeta$-contractive interpolable if and only if it satisfies
-$$
-	\norm{\T \x_i - \T \x_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2, \quad \forall i,j \in [D], \ i \neq j.
-$$
-Therefore, we can define the following constrained regression problem:
-\begin{equation}\label{eq:operator-regression}
-\begin{split}
-	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 \\
-	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \ \forall i,j \in [D], i \neq j
-\end{split}
-\end{equation}
-where again the cost function is a least square terms on the observations and the constraints enforce contractiveness.
-
-\paragraph{Auto-tuning contraction}
-We can modify~\eqref{eq:operator-regression} by including $w = \zeta^2$ as an unknown of the regression problem, which becomes
-\begin{equation}
-\begin{split}
-	\hat{\tv}_i &= \argmin_{\tv_i \in \R^n} \frac{1}{2} \sum_{i \in [D]} \norm{\tv_i - \y_i}^2 + \frac{c}{2} w^2 \\
-	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 - w \norm{\x_i - \x_j}^2 \leq 0 \ \forall i,j \in [D], i \neq j
-\end{split}
-\end{equation}
-this way the contraction constant does not need to be specified, and is \emph{auto-tuned} by the regression.
-
-\paragraph{PRS-based solver}
-.... brief description of basic characteristics, reference to the appendix ....
+[Add here]
 
@@
 
-Let now $\T_k : \R^n \to \R^n$ be a solver for the convex problem observed at time $t_k$, and assume that the operator has a term $\T_{f,k}$ depending exclusively on $f$ (\emph{e.g.} we have $\T_k = \T_k' \circ \T_{f,k}$).
-Since the sampled problem is convex, the solver $\T_k$ is non-expansive (actually, averaged, to guarantee convergence).
+We are now ready to present our main algorithm.
 
-The idea then is to try and learn an approximation of $\T_k$ that is \emph{contractive} rather than non-expansive.
+Having to deal with composite problems $f(\cdot; t_k) + g(\cdot; t_k)$, we focus here on online algorithms of the forward-backward type, i.e., 
+\begin{equation}
+\x_{k+1} = \prox_{g_k} (\x_k - \alpha \nabla_{\x} f_k(\x_k)), \quad k \in \N, \alpha >0.
+\end{equation}
+We let $\T_k = I - \alpha \nabla_{\x} f_k$ be the operator we want to regularize.
+Since $f$ is not smooth strongly convex in general, $\T_k$ is not contractive (in general).
+However, since $g_k$ is convex, the prox operator is non-expansive, so that if $\T_k$ were to be contractive then the forward-backward algorithm would be contracting itself and we could have better convergence guarantees.
 
-Again, w.l.o.g. we are only interested in learning the term $\T_{f,k}$ that depends on $f$. The algorithm can be described as follows: at each time $t_k$ do:
+Therefore, we are interested in learning a contracting $\hat{\T}_k$ by evaluations of $\T_k$. The OpReg-Boost algorithm can be described as follows: at each time $t_k$ do:
 \begin{enumerate}
-	\item sample a new problem, that is, observe $f(\x; t_k)$ and $g(\x; t_k)$;
+	\item Sample a new problem, that is, observe $f(\x; t_k)$ and $g(\x; t_k)$;
 
-	\item approximate the term $\T_{f,k}$ of the solver with a contractive one, and
+	\item Learn the closest contracting operator to $\T_{k}$, say $\hat{\T}_k$ and
 
-	\item apply the resulting solver. For example if $\T_k = \T_k' \circ \T_{f,k}$, then we apply $\T_k = \T_k' \circ \hat{\T}_{f,k}$ where $\hat{\T}_{f,k}$ is the learned operator.
+	\item Apply $\x_{k+1} = \prox_{g_k} (\hat{\T}_k \x_k)$.
 \end{enumerate}
-The learning step is performed using the (novel) constrained operator regression OpReg described in the following.
+The learning step is performed using the (novel) constrained operator regression described in~\eqref{.}, specifically:
 
-In particular we have the following algorithm \nicola{make this pseudo code}
-For $\ell \in 0, 1, \ldots, M$ (for some $M \in \N$):
 \begin{itemize}
-	\item let $\x_k^\ell$ be the current approximate solution, we choose $D-1$ points around it, \emph{e.g.}
-	$$
-		\x_i = \x_k^\ell + \p_i, \ i = 2, \ldots, D, \ \p_i \sim \mathcal{N}(0, \sigma^2 \Im_n)
-	$$
-	and set $\x_1 = \x_k^\ell$;
+	\item Choose $\ell$ points around $\x_k$ including $\x_k$ itself (e.g., adding a zero-mean Gaussian noise term)
 
-	\item we compute the data $\tv_i = \T_{f,k} \x_i$, $i = 1, \ldots, D$, for example $\tv_i = \x_i - \alpha \nabla f(\x_i; t_k)$;
+	\item Evaluate the operator on the data points: $\tv_i = \T_{k} \x_i$, $i\in I_{\ell}$, for example $\tv_i = \x_i - \alpha \nabla_{\x} f(\x_i; t_k)$;
 
-	\item we solve the OpReg, and use the approximate operator at $\x_k^\ell$, that is $\tv_1$, in the chosen solver $\T_k$:
-	$$
-		\x_k^{\ell+1} = \prox_{\alpha g}(\tv_1)
-	$$
-	where $\alpha$ is a step-size.
+	\item Solve~\eqref{eq:operator-regression} with the PRS-based solver, and output $\hat{\tv}_k = \hat{\T}_k \x_k$ to be used in Step 3. of OpReg-Boost.
 \end{itemize}
+
+[Some closing words, no need for interpolation? ]
 
@@
 
+[Add here]
+
 %------------------------------------------------------------------------------
 \section{Numerical Results}\label{sec:numerical}
+
+Wish-list
+
+\begin{itemize}
+\item non-negative Least-squares
+
+\item L1 ?
+
+\item Relative-entropy non-negative regression
+
+\item weakly convex: time-varying phase retrival? (see Convergence of a Stochastic Gradient Method with Momentum for Nonsmooth Nonconvex Optimization)
+
+\end{itemize}
+
+Compare (real-time, gradient/functional calls) with Nesterov, AA, CvxReg-Boost, OpReg-Boost, Gradient descent. Other? (Forward-backward envelope, superMann?)
+
+For the weakly convex one: See Convergence of a Stochastic Gradient Method with Momentum for Nonsmooth Nonconvex Optimization (momentum as described there?)
 
@@
 
-\bibliography{references}
+\newpage
+
+\bibliography{PaperCollection00,references}
 \bibliographystyle{icml2021}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \appendix

### 2021-01-14 paper/main.tex
small things
Third pass

@@
 \DeclareMathOperator{\fix}{fix}
+\DeclareMathOperator{\proj}{proj}
+
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{remark}[theorem]{Remark}
 
@@
 \newcommand{\xx}{\pmb{\xi}}
-
+\newcommand{\ball}[2]{\mathbb{B}_{#2}(#1)}
 \newcommand{\Am}{\mathbold{A}}
@@
 \newcommand{\Pm}{\mathbold{P}}
-
+\newcommand{\cv}{\mathbold{c}}
 \newcommand{\I}{\mathcal{I}}
@@
 \newcommand{\nicola}[1]{{\color{blue}#1}}
+\newcommand{\andrea}[1]{{\color{red}[#1]}}
 
@@
 OpReg-Boost is built to learn the closest algorithm to a given online algorithm that has all the algorithmic properties one needs for fast convergence, and it is based on the concept of operator regression.
-We show how to build OpReg-Boost by using a Peaceman-Rachford solver, and further boost [...
-interpolation-MAP..].
-Simulation results showcase the [better/increase/..] properties of OpReg-Boost w.r.t.
-the more classical [...], and its close relative convex-regression-boost which is also novel but significantly less performing.
+We show how to compute OpReg-Boost by using a Peaceman-Rachford solver, and further trade-off computations and accuracy with an interpolation-based technique based on alternating projection.
+Simulation results showcase the \andrea{better/increase/..} properties of OpReg-Boost w.r.t.
+the more classical \andrea{...}, and its close relative convex-regression-boost (CvxReg-Boost) which is also novel but significantly less performing.
 \end{abstract}
@@
 
-[Add others' papers, esp. ML community]
+\andrea{Add others' papers, esp. ML community}
+
+\andrea{Notation to iron}
 
@@
 
-Solving time-varying optimization problems with online algorithms amounts to find and track continuously changing optimizers.
-If we let the optimizers trajectory be defined as $\x^*(t)$, a significant results for online algorithms in this context is that if the \emph{path-length} $\sum_{k=1}^T \|\x^*(t_{k+1}) - \x^*(t_{k})\|$, for subsequent time instances $t_{k+1}, t_k$, is not sub-linear in $T$, then online algorithms will have an asymptotical error $O(1)$~\cite{Besbes2013, Jadbabaie2015, SPM, NaLi2020} (or $O(T)$ in terms of pertinent notions of regret)\footnote{
+Solving time-varying optimization problems with online algorithms amounts to find and track continuously changing optimizers $\x^*(t)$ and optimal values $F^*(t)$.
+A significant results for discrete-time online algorithms, that sample and solve sequences of time-varying problems at discrete time-instances $t_k$, $k \in N$, is that if the variations of the problem in time are not vanishing, then online algorithms will have an asymptotical error in terms of optimality, depending on those variations~\cite{Besbes2013, Jadbabaie2015, SPM, NaLi2020}\footnote{
 %%% Footnote Jadbabaie:
-In~\cite{Jadbabaie2015} and subsequent works, [Finish]
+In~\cite{Jadbabaie2015} and subsequent works, these asymptotical error is formulated in terms of a pertinent notion of regret, and the variations in terms of path-length and functional variability.
 %%%
@@
 
-This gives rise to convex-regression-based boosting.
+This gives rise to convex-regression-based boosting, or CvxReg-Boost.
 
@@
 %%
-\item We present efficient ways to solve the operation regression problem via a pertinent reformulation of the Peaceman-Rachford splitting method. [.. more ]
+\item We present efficient ways to solve the regression problems via a pertinent reformulation of the Peaceman-Rachford splitting (PRS) method.
+Our PRS method is trivially parallel and allows for a reduction of the per iteration complexity from $O()$ to $O()$, where \andrea{put in the numbers}.
 %%
-\item We [Interpolation]
+\item We show how to make use of an 1945 interpolation technique to trade-off accuracy and speed in operation regression, by interpolating the learned operator outside the data points via alternating projections.
 %%
-\item We showcase the [simulation results]
+\item We showcase the \andrea{simulation results}
 \end{enumerate}
@@
 \subsection{Literature review}
+
+\andrea{add ML work}
 
@@
 
-The acceleration schemes that we compare with are [Tell and cite] e.g., AA: \cite{pmlr-v119-mai20a}
+The acceleration schemes that we compare with are \andrea{Tell and cite, e.g., AA: \cite{pmlr-v119-mai20a}}
 
@@
 
-The prox operator [..]
+We indicate with $\prox_{\alpha g}(\cdot)$ the proximal operator of function $g$, and with $\proj_{C}(\cdot)$, the projection operator onto the set $C$.
 
@@
 \begin{equation}\label{eq:continuous-time-problem}
-	\x^*(t) \in \argmin_{\x} f(\x; t) + g(\x; t)
+	\x^*(t) \in \argmin_{\x} f(\x; t) + g(\x; t) =: F(\x; t)
 \end{equation}
@@
 \end{equation}
-Our overarching goal is to set up an online algorithm $\mathcal{A}$ that generate a sequence of approximate optimizers $\{\x_k\}_{k\in \N}$, such that the asymptotical tracking error 
+Our overarching goal is to set up an online algorithm of the forward-backward type,
+\begin{equation}
+\x_{k+1} = \prox_{\alpha g(\cdot, t_k)} (\x_k - \alpha \nabla_{\x} f(\x_k; t_k)), \quad k \in \N,
+\end{equation}
+that generate a sequence of approximate optimizers $\{\x_k\}_{k\in \N}$, such that the asymptotical tracking error \andrea{
 \begin{equation}
@@
 
-The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online algorithm $A$ (here a forward-backward algorithm) can obtain linear convergence to the asymptotical error bound $\Delta/(1-\gamma)$, with optimal $\gamma = \frac{L-m}{L+m}$; much weaker results hold for the general convex case~\cite{Simonetto20XX}, for example [..]
+Here should we formulate it in terms of functional $|f - f^*|$ instead? Let's discuss.
 
-The second important result is that even a simple Tikhonov regularization $+ \frac{w}{2} \|x\|^2_2$, transforming a smooth but not strongly convex case into a strongly convex one allows for a boost in convergence and [..]
+Somewhere we have to say that forward-backward may not converge in general, while here we ensure convergence since we are convex. This is an important point
 
-%% say something more, change?
+}
+
+\andrea{Explain a bit better what we mean by online-- I think we could be clearer?? Or maybe in the introduction.}
+
+\andrea{Is $f$ differentiable, does it have to be?}
+
+The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online forward-backward algorithm can obtain linear convergence to the asymptotical error bound $\limsup_{k\to\infty}\|\x_k - \x^*(t_k)\| \leq \gamma\Delta/(1-\gamma)$, with optimal $\gamma = \frac{L-m}{L+m}$; much weaker results hold for the general convex case~\cite{Simonetto20XX}.
+
+The second important result is that even a simple Tikhonov regularization $+ \frac{w}{2} \|x\|^2_2$, transforming the above $f \in \mathcal{S}_{m,L}(\R^n)$ to $f' \in \mathcal{S}_{m',L'}(\R^n)$ with a better $\gamma'<\gamma$, could allow for a boost in convergence and reducing the asymptotical error.
+In fact, if the optimizers of the true function $F = f+g$ and regularized function $F' = f'+g$ are never farther apart than $e_{\x}$, then the asymptotical error for an algorithm on $F'$ is $\gamma'\Delta'/(1-\gamma') + e_{\x}$, which can be less than the original $\gamma\Delta/(1-\gamma)$.
+
+\andrea{say something more, change above -- these are worst case bounds..?}
 
@@
 
+In the following, we will explore both Q1 and Q2, with a special emphasis on Q2, since it provides better results in simulations.
+
 \section{Q1. Convex Regression}
@@
 We briefly introduce here the concept of convex regression, while we leave the main technical details to~\cite{Mazumder2019,simonetto_smooth_2021}.
-Suppose one has collected $\ell$ noisy measurements of a convex function $\varphi(\x): \R^n \to \R$ (say $y_i$) at points $\x_i \in \R^n$, $i \in I_{\ell}$.
+Suppose one has collected $\ell$ noisy measurements of a convex function $\varphi(\x): \R^n \to \R$ (say $y_i$) at points $\x_i \in \R^n$, $i \in I_{\ell}$, and (optionally) its gradients $\nabla_{\x} \varphi(\x_i)$.
 Then convex regression is a least-squares approach to estimate the generating function based on the measurements.
@@
 \begin{equation}\label{eq.inf}
-\hat{\varphi}_{\ell} \in \argmin_{\psi \in \mathcal{S}_{m, L}(\R^n)}\Big\{ \sum_{i\in I_{\ell}} (y_i - \psi(\x_i))^2 \Big\} \,.
+\hat{\varphi}_{\ell} \in \argmin_{\psi \in \mathcal{S}_{m, L}(\R^n)}\Big\{ \sum_{i\in I_{\ell}} (y_i - \psi(\x_i))^2 + \|\z_i - \nabla_{\x} \psi(\x_i)\|^2 \Big\} \,,
 \end{equation}
+where $y_i$ and $\z_i$ are the measurements of the function and the gradients at the data points.
 
@@
 \begin{eqnarray}
-(\f^*, \bdelta^*) &&= \argmin_{\f\in\R^\ell\!,~ \bdelta \in\R^{n\ell}} \sum_{i\in I_{\ell}} (y_i - \varphi_i)^2 \\
+(\f^*, \bdelta^*) &&\hskip-.5cm= \argmin_{\f\in\R^\ell\!,~ \bdelta \in\R^{n\ell}} \sum_{i\in I_{\ell}} (y_i - \varphi_i)^2 + \|\z_i - \bdelta_i \|^2 \\
 \mathrm{s.t.:} &&
@@
 
-Then, to solve Q1, one could consider a number of evaluations of the function $f(\x; t_k)$ as noisy measurements of an underlying convex function $\varphi_k \in \mathcal{S}_{m,L}(\R^n)$ and using the least-squares approach above to \emph{project} function $f(\cdot; t_k)$ onto the space of ``good'' functions [Complete..
-put the details in the appendix]
+Then, to solve Q1, one could consider, for each time $t_k$, a number of evaluations of the function $f(\x; t_k)$ (and optionally its gradients) as noisy measurements of an underlying convex function $\hat{f}_k \in \mathcal{S}_{m,L}(\R^n)$ and using the least-squares approach above to \emph{project} function $f(\cdot; t_k)$ onto the space of ``good'' functions $\mathcal{S}_{m,L}(\R^n)$.
+Then, one can use the estimated function $\hat{f}_k$ and its estimated gradients to perform a step of the algorithm.
+
+We include in the appendix all the technical details of such CvxReg-Boost algorithm, while we focus now on solving Q2 via operator regression, which is ultimately better performing.
+
+\andrea{I think it's not super clear-- Add the algorithm here and the explanation of the compl. complexity and other in the appendix ? }
 
@@
 where $\T_k: \R^n \to \R^n$ is the gradient algorithm operator.
-Interpreting algorithms as operators (possibly averaged, monotone, etc.) has been extremely fruitful for characterizing their convergence properties~\cite{Rockafellar1976, Eckstein1989, bauschke_convex_2017,Ryu2015,tom-also}.
+Interpreting algorithms as operators (possibly averaged, monotone, etc.) has been extremely fruitful for characterizing their convergence properties~\cite{Rockafellar1976, Eckstein1989, bauschke_convex_2017,Ryu2015,Sherson2018}.
 
@@
 where again the cost function is a least square terms on the ``observations''' and the constraints enforce contractiveness.
-In particular, the optimal values $\hat{\tv}$ on the data points represent the evaluations of a $\zeta$-contracting operator when applied to those points.
+In particular, the optimal values $\hat{\tv}$ on the data points represent the evaluations of a $\zeta$-contracting operator when applied to those points, i.e., $\hat{\tv}_i = \hat{\T}_k\x_i$.
 
-To extend [interpolation here]
+To extend the operator outside the data points in the whole space, we can use a 1945 results, and namely the Corollary to Theorem~5 of \cite{valentine_lipschitz_1945}.
+In particular, we are interested in interpolating a Lipschitz continuous operator (that is, non-expansive or contractive) from a set of evaluations.
+The data are the pairs $\{ (\x_i, \hat{\tv}_i) \}_{i \in I_{\ell}}$.
 
-%% Then Interpolation here..
+By the Corollary to Theorem~5 of \cite{valentine_lipschitz_1945}, we know that a $\zeta$-Lipschitz continuous map $\hat{\T}_k$ can be extended (that is, interpolated) in a new point $\x$, while preserving Lipschitz continuity $\zeta$, by the construction:
+\begin{equation}\label{eq:interpolation}
+	\hat{\T}_k \x = \begin{cases}
+		\hat{\tv}_i & \text{if} \ \x = \x_i \\
+		\hat{\tv} \in \bigcap_{i \in I_{\ell}} \ball{\hat{\tv}_i}{\zeta \norm{\x - \x_i}} & \text{otherwise}
+	\end{cases}
+\end{equation}
+where $\ball{\cv}{r} \subset \R^n$ denotes a ball of center $\cv$ and radius $r$.
+That is, we can interpolate $\hat{\T}_k$ in a new point $\x$ by finding a point in the intersection of the balls centered in $\hat{\tv}_i$ with radius $\zeta \norm{\x - \x_i}$, $i = 1, \ldots, \ell$.
+Notice that the intersection $\bigcap_{i \in I_{\ell}} \ball{\hat{\tv}_i}{\zeta \norm{\x - \x_i}}$ is guaranteed to be non-empty by Theorem~1 of \cite{valentine_lipschitz_1945}.
+
+By definition $\hat{\tv}$ satisfies
+\begin{equation}
+	\norm{\hat{\tv} - \hat{\tv_i}} \leq \zeta \norm{\x - \x_i}, \quad \forall i \in I_{\ell},
+\end{equation}
+which implies that Lipschitz continuity (and contractivity) is preserved.
+
+\andrea{What happens to $\|\tv' - \tv''\|$ for $\x'$ and $\x''$ both interpolated? }
+
+Interpolating a Lipschitz continuous operator requires therefore finding a point in the intersection of $\ell$ ball sets.
+In the Appendix [..], we show how to efficiently compute this intersection with the method of alternating projections~\cite{reich_projection_2015}.
 
 \subsection{Optional auto-tuning }
+
+\andrea{Appendix?}
 
@@
 
-[Add here]
+The solution of the convex problem~\eqref{eq:operator-regression} can be obtained by off-the-shelf solvers, but generally the computational complexity can be a limiting factor, since the problem has a number of constraints that scales quadratically with the number of data points $\ell$.
+In particular, the computational complexity of interior-point methods would scale as $O()$.
+This is generally the case in non-parametric regression~\cite{.}.
+
+Here, we propose a trivially parallel tailored-made algorithm that solves~\eqref{eq:operator-regression} more efficiently (formally .. [..]) based on Peaceman-Rachford splitting (PRS).
+
+The idea is as follows: each pair of data points $i, j \in I_{\ell}$, $i \neq j$, gives rise to one constraint, for a total of $\ell(\ell-1)/2$ constraints. We define the following set of pairs
+\begin{equation}
+	\mathcal{V} = \left\{ e = (i,j) \ | \ i, j \in I_{\ell}, \ i < j \right\}
+\end{equation}
+which are ordered (that is, for example we take $(1,2)$ and not $(2,1)$, to avoid counting constraints twice).
+To each pair $e = (i,j)$ corresponds the constraint $\norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2$.
+
+Let $\tv_{i,e}$ and $\tv_{j,e}$ be copies of $\tv_i$ and $\tv_j$ associated to the $e$-th constraint; then we can equivalently reformulate Problem~\eqref{eq:operator-regression} as
+\begin{subequations}\label{eq:equivalent-problem}
+\begin{align}
+	&\min_{\tv_{i,e}, \tv_{j,e}} \frac{1}{2 (\ell-1)} \sum_{e \in \mathcal{V}} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 \\
+	&\text{s.t.} \ \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \label{eq:interpolation-constraints} \\
+	&\qquad \tv_{i,e} = \tv_{i,e'} \ \forall e, e' | i \sim e, e'. \label{eq:consensus-constraints}
+\end{align}
+\end{subequations}
+Problem~\eqref{eq:equivalent-problem} is a strongly convex problem with convex constraints defined in the variables $\tv_{i,e}$.
+
+Let $\xx$ be the vector stacking all the $\tv_{i,e}$, then the problem is equivalent to
+\begin{align*}
+	\min_{\xx} \psi(\xx) + \chi(\xx)
+\end{align*}
+where
+$$
+	\psi(\xx) = \frac{1}{2(\ell-1)} \norm{\xx - \y}^2 + \psi_1(\xx)
+$$
+with $\psi_1$ the indicator function imposing~\eqref{eq:interpolation-constraints} and $\xi$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}.
+The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
+\begin{subequations}
+\begin{align}
+	&\xx^j = \prox_{\rho \psi}(\z^j) \label{eq:prs-xi} \\
+	&\vv^j = \prox_{\rho \chi}(2 \xx^j - \z^j) \\
+	&\z^{j+1} = \z^j + \vv^j - \xx^j.
+\end{align}
+\end{subequations}
+The proximal of $\chi$ corresponds to the projection onto the consensus space, and thus can be characterized simply by
+$$
+	\vv_{i,e}^j = \frac{1}{\ell-1} \sum_{e' | i \sim e'} \left( 2 \tv_{i,e'}^j - \z_{e'}^j\right).
+$$
+Regarding the proximal of $\psi$, $\psi$ is separable, in the sense that it can be written as
+$$
+	\psi(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right]
+$$
+where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints} \andrea{is it $\psi_1$?}.
+Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
+\begin{equation}\label{eq:local-updates}
+\begin{split}
+	(\tv_{i,e},\tv_{j,e}) &= \argmin_{\tv_{i,e},\tv_{j,e}} \left\{ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \right.\\ & \left.\qquad \frac{1}{2\rho} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \z_e^j}^2 \right\}\\
+	&\text{s.t.} \quad \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2.
+\end{split}
+\end{equation}
+Problems~\eqref{eq:local-updates} are convex QCQP with one constraint, and can be solved in the dual domain as scalar problems by using Newton's method~\cite{.}, yielding a total computational complexity of $O(..)$ for the solution of~\eqref{.}.
 
@@
 
-Therefore, we are interested in learning a contracting $\hat{\T}_k$ by evaluations of $\T_k$. The OpReg-Boost algorithm can be described as follows: at each time $t_k$ do:
+Therefore, we are interested in learning a contracting $\hat{\T}_k$ by evaluations of $\T_k$. The OpReg-Boost algorithm can be described as follows.
+
+\smallskip
+\smallskip
+\hrule
+{\bf OpReg-Boost algorithm}
+\smallskip
+\hrule
+{\bf Required:} number of points $\ell$, stepsize $\alpha$, contraction factor $\zeta$, initial condition $\x_0$.
+
+At each time $t_k$ do:
 \begin{enumerate}
 	\item Sample a new problem, that is, observe $f(\x; t_k)$ and $g(\x; t_k)$;
-
-	\item Learn the closest contracting operator to $\T_{k}$, say $\hat{\T}_k$ and
-
-	\item Apply $\x_{k+1} = \prox_{g_k} (\hat{\T}_k \x_k)$.
-\end{enumerate}
-The learning step is performed using the (novel) constrained operator regression described in~\eqref{.}, specifically:
-
+	\item Learn the closest contracting operator to $\T_{k}$, say $\hat{\T}_k$ by:
+	%%
 	\begin{itemize}
 		\item Choose $\ell$ points around $\x_k$ including $\x_k$ itself (e.g., adding a zero-mean Gaussian noise term)
+		\item Evaluate the operator on the data points: $\tv_i = \T_{k} \x_i$, $i\in I_{\ell}$, i.e., $\tv_i = \x_i - \alpha \nabla_{\x} f(\x_i; t_k)$;
+		\item Solve~\eqref{eq:operator-regression} with the PRS-based solver, and output $\hat{\tv}_k = \hat{\T}_k \x_k$,
+\end{itemize}
+	%%
+	\item Apply $\x_{k+1} = \prox_{g_k} (\hat{\T}_k \x_k) = \prox_{g_k} (\hat{\tv}_k) $.
+\end{enumerate}
+\smallskip
+\hrule
 
-	\item Evaluate the operator on the data points: $\tv_i = \T_{k} \x_i$, $i\in I_{\ell}$, for example $\tv_i = \x_i - \alpha \nabla_{\x} f(\x_i; t_k)$;
+A couple of words are now in order.
+First, the computational complexity of the algorithm is dominated by the operation regression problem~\eqref{eq:operator-regression}, while its number of gradient calls is $\ell$-times the ones of a standard forward-backward algorithm.
+At each time $t_k$, we perform $\ell$ gradient evaluations.
+We remark that $\ell$ can be as small as $5$ in practice.
 
-	\item Solve~\eqref{eq:operator-regression} with the PRS-based solver, and output $\hat{\tv}_k = \hat{\T}_k \x_k$ to be used in Step 3. of OpReg-Boost.
-\end{itemize}
+Second, as one can see from step 3., there is no need for solving the interpolation problem~\eqref{eq:interpolation}, since the operation regression problem~\eqref{eq:operator-regression} already provides the evaluation of the regularized operator at the data point $\x_k$.
 
-[Some closing words, no need for interpolation? ]
+In an attempt to reduce gradient calls, we present next an interpolated version of OpReg-Boost.
 
@@
 
-[Add here]
+\andrea{Add intro}
+
+\smallskip
+\smallskip
+\hrule
+{\bf OpReg-Boost with interpolation algorithm}
+\smallskip
+\hrule
+{\bf Required:} number of points $\ell$, stepsize $\alpha$, initial condition $\x_0$, interpolation steps $\tau$.
+
+At each time $t_k$ do:
+\begin{enumerate}
+	\item Sample a new problem, that is, observe $f(\x; t_k)$ and $g(\x; t_k)$;
+	\item {\bf IF} $k \,\textrm{mod}\, \tau = 0$ then, 
+	\begin{enumerate}
+	\item Learn the closest contracting operator to $\T_{k}$, say $\hat{\T}_k$ by:
+	%%
+	\begin{itemize}
+		\item Choose $\ell$ points around $\x_k$ including $\x_k$ itself (e.g., adding a zero-mean Gaussian noise term)
+		\item Evaluate the operator on the data points: $\tv_i = \T_{k} \x_i$, $i\in I_{\ell}$, i.e., $\tv_i = \x_i - \alpha \nabla_{\x} f(\x_i; t_k)$;
+		\item Solve~\eqref{eq:operator-regression} with the PRS-based solver, and output $\hat{\tv}_k = \hat{\T}_k \x_k$,
+\end{itemize}
+\end{enumerate}
+	{\bf ELSE},
+	\begin{enumerate}
+	\item Interpolate last available $\hat{\T}_t$ for $\tv_k = \x_k - \alpha \nabla_{\x} f(\x_k; t_k)$ by using~\eqref{eq:interpolation} with the method of alternating projections and output $\hat{\tv}_k$
+\end{enumerate}
+	%%
+	\item Apply $\x_{k+1} = \prox_{g_k} (\hat{\tv}_k) $.
+\end{enumerate}
+\smallskip
+\hrule
+
+\andrea{add explanation and closure.}
 
@@
 %------------------------------------------------------------------------------
+\section{CvxReg-Boost}
+
+\andrea{[Write here cvx reg boost.. and algorithm.]}
+
+%------------------------------------------------------------------------------
 \section{PRS-Based QCQP solver}
@@
 
-The idea is as follows: each pair of data points $i, j \in [D]$, $i \neq j$, gives rise to one constraint, for a total of $D(D-1)/2$ constraints. We define the following set of pairs
-$$
-	\mathcal{V} = \left\{ e = (i,j) \ | \ i, j \in [D], \ i < j \right\}
-$$
-which are ordered (that is, for example we take $(1,2)$ and not $(2,1)$, to avoid counting constraints twice).
-Clearly to each pair $e = (i,j)$ corresponds the constraint $\norm{\tv_i - \tv_j}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2$.
-
-Let now $\tv_{i,e}$ and $\tv_{j,e}$ be copies of $\tv_i$ and $\tv_j$ associated to the $e$-th constraint; then we can equivalently reformulate the OpReg~\eqref{eq:operator-regression} as
-\begin{subequations}\label{eq:equivalent-problem}
-\begin{align}
-	&\min_{\tv_{i,e}, \tv_{j,e}} \frac{1}{2 (D-1)} \sum_{e \in \mathcal{V}} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 \\
-	&\text{s.t.} \ \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2 \label{eq:interpolation-constraints} \\
-	&\qquad \tv_{i,e} = \tv_{i,e'} \ \forall e, e' | i \sim e, e'. \label{eq:consensus-constraints}
-\end{align}
-\end{subequations}
-Clearly~\eqref{eq:equivalent-problem} is a strongly convex problem with convex constraints defined in the variables $\tv_{i,e}$.
-
-%----------------------------------------
-\subsection{PRS solver}
-Let $\xx$ be the vector stacking all the $\tv_{i,e}$, then the problem is equivalent to
-\begin{align*}
-	\min_{\xx} f(\xx) + g(\xx)
-\end{align*}
-where
-$$
-	f(\xx) = \frac{1}{2(D-1)} \norm{\xx - \y}^2 + f_1(\xx)
-$$
-with $f_1$ the indicator function imposing~\eqref{eq:interpolation-constraints} and $g$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}.
-The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
-\begin{subequations}
-\begin{align}
-	&\xx^\ell = \prox_{\rho f}(\z^\ell) \label{eq:prs-xi} \\
-	&\vv^\ell = \prox_{\rho g}(2 \xx^\ell - \z^\ell) \\
-	&\z^{\ell+1} = \z^\ell + \vv^\ell - \xx^\ell.
-\end{align}
-\end{subequations}
-The proximal of $g$ corresponds to the projection onto the consensus space, and thus can be characterized simply by
-$$
-	\vv_{i,e}^\ell = \frac{1}{D-1} \sum_{e' | i \sim e'} \left( 2 \tv_{i,e'}^\ell - \z_{e'}^\ell\right).
-$$
-Regarding the proximal of $f$, is is clear that $f$ is separable, in the sense that it can be written as
-$$
-	f(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (D-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right]
-$$
-where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints}. Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
-\begin{equation}\label{eq:local-updates}
-\begin{split}
-	(\tv_{i,e},\tv_{j,e}) &= \argmin \left\{ \frac{1}{2 (D-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \frac{1}{2\rho} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \z_e^\ell} \right\}\\
-	&\text{s.t.} \quad \norm{\tv_{i,e} - \tv_{j,e}}^2 \leq \zeta^2 \norm{\x_i - \x_j}^2.
-\end{split}
-\end{equation}
+[Maybe here specify the Newton's step?]
 
@@
 %------------------------------------------------------------------------------
-\section{Interpolation Using MAP}
+\section{Interpolating a Lipschitz continuous operator}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% INTERPOLATION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We will be discussing possible methods to solve the interpolation problem~\eqref{eq:interpolation} to select the most efficient strategy.
+Problem~\eqref{eq:interpolation} is a \emph{feasibility problem}, that is, it requires that we find a point in the intersection of closed, convex sets.
+There are several algorithms for solving this class of problems, \emph{e.g.} the method of alternating projections (MAP) and Peaceman-Rachford splitting, see \cite{reich_projection_2015} for a review.
+
+Moreover, the feasibility problem~\eqref{eq:interpolation} can also be solved using \emph{best approximation methods}, which find the point in the intersection that is closest to a given vector.
+Of course best approximation problems are more difficult than feasibility ones.
+The literature on best approximation is very vast, see \emph{e.g.} \cite{reich_projection_2015}, Chapter~30 of \cite{bauschke_convex_2017}, \cite{artacho_new_2018} and references therein.
+
+Finally, given the fact that~\eqref{eq:interpolation} requires a point in the intersection of balls, we may use methods that are tailored to the particular structure of ball sets, \emph{e.g.} \cite{lushchakova_geometric_2020}.
+
+\subsection{Comparison}
+The numerical results reported in the here are derived in the following set-up.
+We generate $\ell$ intersecting ball sets in $\R^n$, with radii randomly picked in $(0, 100)$.
+The centers of the balls are randomly chosen so that the sets include the origin, and are thus guaranteed to intersect at least in that point.
+
+In Figure~\ref{fig:projection_methods} we report a comparison of three feasibility methods -- alternating projections (MAP), parallel projections (PP), Peaceman-Rachford splitting(PRS) \cite{reich_projection_2015,bauschke_convex_2017} -- and two best approximation methods -- Halpern and Haugazeau methods \cite{bauschke_convex_2017}.
+The simulations are performed choosing a number of points $\ell = 50$ in dimension $n = 5$.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width = 0.9\columnwidth]{Figures/comparison_projection_methods}
+\caption{Comparison of feasibility and best approximation methods.}
+\label{fig:projection_methods}
+\end{figure}
+
+As we can see, MAP is by far the fastest of the methods, reaching convergence (with tolerance $10^{-14}$) in just $33$ iterations.
+Parallel projections and Peaceman-Rachford splitting reach convergence in $1930$ and $1036$ iterations, respectively, while the best approximation methods are still far from converging after $50000$ iterations.
+
+MAP not only achieves superior convergence speed, but it is also the simplest of the methods in terms of computational complexity, see \emph{e.g.} \cite{reich_projection_2015}.
+Therefore we select MAP for our interpolation problem.
+
+\begin{remark}
+Although MAP achieves extremely fast convergence when applied to~\eqref{eq:interpolation}, this is by no means true in general; indeed, it is possible to show that MAP has \emph{arbitrarily slow} convergence in some scenarios, see for example \cite{hundal_alternating_2004,bauschke_characterizing_2009}.
+\end{remark}
+
+%------------------------------------------
+\subsection{How fast is MAP?}
+As shown in the previous section, solving~\eqref{eq:interpolation} using the method of alternating projections is very effective. Recall that the MAP is characterized by the following update
+\begin{equation}\label{eq:alternating_projections}
+	\x^{j+1} = (\proj_{\ball{\cv_{\ell}}{r_{\ell}}} \circ \cdots \proj_{\ball{\cv_1}{r_1}}) \x^j, \quad j \in \N
+\end{equation}
+for any initial condition $\x^0 \in \R^n$.
+
+In Figure~\ref{fig:map-histogram} we report an histogram of the number of iterations that MAP required to converge, with $\ell = 100$ and $n = 25$.
+The histogram is computed using data from $10000$ repetitions, each repetition being characterized by a different set of randomly generated balls.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width = 0.9\columnwidth]{Figures/MAP_histogram}
+\caption{Histogram of iterations required by MAP over $10000$ repetitions.}
+\label{fig:map-histogram}
+\end{figure}
+
+As we can see, in almost one quarter of the repetitions MAP required a single iteration to converge, while the remaining number of iterations occur $\sim 500$ or less.
+In particular, the maximum number of iterations is $86$, and the mean is approximately $13 \pm 11$.
+
+In Figure~\ref{fig:map-changing-d} instead we evaluate the effect of the number of balls on the speed of MAP.
+For each value of $\ell$ between $2$ and $100$ we perform $10000$ repetitions of MAP, each repetition being characterized by a different random set of balls.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width = 0.9\columnwidth]{Figures/MAP_changing_d}
+\caption{Histogram of iterations required by MAP over $10000$ repetitions.}
+\label{fig:map-changing-d}
+\end{figure}
+
+As we can see, the mean number of iterations required by MAP grows as the $\log(\ell)$, in particular as $2.84 \log(\ell)$ (dashed curve).
+Even though a larger number of sets increases the number of iterations, this number is still very small (in mean) even for $\ell = 100$.
 

### 2021-01-14 reg4opt/operators.py
updated operators sub-module

@@ -8,6 +8,8 @@ Operator template and examples.
 import numpy as np
 from numpy import linalg as la
 
+from tvopt import sets
+
 
 #%% FUNCTION TEMPLATE
 
@@ -44,9 +46,10 @@ class Operator():
     rng : tvopt.sets.Set
         The operator's range.
     time : tvopt.sets.T
-        The time domain :math:`\mathbb{R}_+`. If the cost is static this is None.
+        The time domain :math:`\mathbb{R}_+`. If the operator is static this is
+        None.
     is_dynamic : bool
-        Attribute to check if the cost is static or dynamic.
+        Attribute to check if the operator is static or dynamic.
     """
     
     def __init__(self, dom, rng=None, time=None):
@@ -174,7 +177,7 @@ class Operator():
         Parameters
         ----------
         t : float
-            The time at which the cost should be sampled.
+            The time at which the operator should be sampled.
 
         Returns
         -------
@@ -201,6 +204,160 @@ class Operator():
             return ScaledOperator(self, c)
         else:
             raise TypeError("Can't multiply Operator by {}.".format(type(c)))
+
+
+# -------- SPECIAL OPERATORS
+
+class SeparableOperator(Operator):
+    r"""
+    Separable operator.
+
+    This class defines a separable operator, that is
+    
+    .. math:: \mathcal{T}(\pmb{x}; t) = \begin{bmatrix} \vdots \\ \mathcal{T}_i(x_i; t) \\ \vdots \end{bmatrix}
+    
+    where :math:`x_i \in \mathbb{R}^{n_1 \times n_2 \times \ldots}` for each
+    :math:`i = 1, \ldots, N`. Each of the component operators :math:`T_i` can
+    be either static or dynamic. This is useful for defining distributed
+    optimization problems.
+    
+    The overall dimension of the domain is 
+    :math:`n_1 \times n_2 \times \ldots \times N`, meaning that the last 
+    dimension indexes the components.
+    
+    The class exposes the same methods as any `Operator`, with the difference 
+    that the keyword argument `i` can be used to evaluate only a single component.
+    If all components are evaluated, an ndarray is returned with the last
+    dimension indexing the components.
+
+    The class has the `Operator` attributes, with the following additions.
+    
+    Attributes
+    ----------
+    ops : list
+        The component operators.
+    N : int
+        The number of components.
+    is_dynamic : bool
+        True if at least one component is dynamic.
+    """
+    
+    def __init__(self, ops):
[…]

### 2021-01-14 reg4opt/operators.py
updated docs

@@ -53,7 +53,7 @@ class Operator():
     """
     
     def __init__(self, dom, rng=None, time=None):
-        """
+        r"""
         Class constructor.
 
         Parameters
@@ -71,7 +71,7 @@ class Operator():
         self.rng = rng if rng is not None else self.dom
         
     def operator(self, x, *args, **kwargs):
-        """
+        r"""
         An evaluation of the operator.
 
         Parameters
@@ -88,7 +88,7 @@ class Operator():
         raise NotImplementedError()
     
     def fpr(self, x, *args, **kwargs):
-        """
+        r"""
         Evaluate the fixed point residual (FPR).
         
         This method returns the FPR
@@ -114,7 +114,7 @@ class Operator():
         return la.norm(x - self.operator(x, *args, **kwargs))
     
     def compose(self, other):
-        """
+        r"""
         Compose the operator with a second one.
         
         The method composes the operator with a second one, provided that the
@@ -138,7 +138,7 @@ class Operator():
         return CompositeOperator(self, other)
     
     def average(self, a):
-        """
+        r"""
         Averaging (a.k.a. relaxation) of the operator.
         
         The method returns an averaged version of the operator, defined as
@@ -166,7 +166,7 @@ class Operator():
         return AveragedOperator(self, a)
     
     def sample(self, t):
-        """
+        r"""
         Sample the operator.
         
         This method returns a `SampledOperator` object which consists of the
@@ -243,7 +243,7 @@ class SeparableOperator(Operator):
     """
     
     def __init__(self, ops):
-        """
+        r"""
         Class constructor.
 
         Parameters
@@ -260,7 +260,7 @@ class SeparableOperator(Operator):
         self.ops, self.N = ops, len(ops)
     
     def operator(self, x, *args, i=None, **kwargs):
-        """
+        r"""
         An evaluation of the separable operator.
         
         This method performs an evaluation of the component operators. If the 
@@ -309,7 +309,7 @@ class DiscreteDynamicOperator(Operator):
     """
     
     def __init__(self, ops, t_s=1):
-        """
+        r"""
         Class constructor.
         
         Creates the dynamic operator, optionally using the specified sampling
@@ -340,7 +340,7 @@ class DiscreteDynamicOperator(Operator):
         return self.ops[self.time.check_input(t)].operator(x, **kwargs)
 
     def sample(self, t):
-        """
+        r"""
         Sample the operator.
         
[…]

### 2021-01-15 paper/main.tex
Third pass ++

@@
 
-An operator $\T: \R^n \to \R^n$ is said to be non-expansive iff $\|T \x - T \y \| \leq \|\x- \y\|$, for all $\x, \y \in \R^n$, whereas it is $\zeta$-contractive, $\zeta\in(0,1)$, iff $\|T \x - T \y \| \leq \zeta \|\x- \y\|$, for all $\x, \y \in \R^n$.
+An operator $\T: \R^n \to \R^n$ is said to be non-expansive iff $\|T \x - T \y \| \leq \|\x- \y\|$, for all $\x, \y \in \R^n$, whereas it is $\zeta$-contractive, $\zeta\in(0,1)$, iff $\|\T \x - \T \y \| \leq \zeta \|\x- \y\|$, for all $\x, \y \in \R^n$.
 
-We indicate with $\prox_{\alpha g}(\cdot)$ the proximal operator of function $g$, and with $\proj_{C}(\cdot)$, the projection operator onto the set $C$.
+We indicate with $\prox_{\alpha g}(\cdot)$ the proximal operator of function $g$ with parameter $\alpha>0$, and with $\proj_{C}(\cdot)$, the projection operator onto the set $C$.
 
@@
 \begin{equation}\label{eq:continuous-time-problem}
-	\x^*(t) \in \argmin_{\x} f(\x; t) + g(\x; t) =: F(\x; t)
+	\x^*(t) \in \argmin_{\x \in \R^n} f(\x; t) + g(\x; t) =: F(\x; t)
 \end{equation}
@@
 \begin{equation}\label{eq:base-problem}
-	\x^*(t_k) \in \argmin_{\x} f(\x; t_k) + g(\x; t_k), \qquad k \in \N. 
+	\x^*(t_k) \in \argmin_{\x \in \R^n} f(\x; t_k) + g(\x; t_k), \qquad k \in \N. 
 \end{equation}
-Our overarching goal is to set up an online algorithm of the forward-backward type,
-\begin{equation}
-\x_{k+1} = \prox_{\alpha g(\cdot, t_k)} (\x_k - \alpha \nabla_{\x} f(\x_k; t_k)), \quad k \in \N,
-\end{equation}
-that generate a sequence of approximate optimizers $\{\x_k\}_{k\in \N}$, such that the asymptotical tracking error \andrea{
+The overarching goal of time-varying optimization is to set up an online algorithm $\mathcal{A}$ that generate a sequence of approximate optimizers $\{\x_k\}_{k\in \N}$, such that the asymptotical tracking error
 \begin{equation}
@@
 \end{equation}
-is as small as possible. Our main blanket assumption is that optimizers\footnote{..} at subsequent time instances cannot be arbitrarily far apart, that is, 
+is as small as possible. The main blanket assumption is that there exists an optimizer trajectory $\x^*(t)$ such that,
 \begin{equation}
@@
 \end{equation}
-which in turn guarantees that the path-length grows linearly in time, 
-\begin{equation}
-\sum_{k\in \N} \|\x^*(t_{k+1}) - \x^*(t_k)\| \leq \Delta k.
+which means that the optimizers can be tracked.
+
+To fix the ideas, we focus here on online algorithms of the forward-backward type, i.e., for each $t_{k+1}$ we update the sequence $\{\x_k\}_{k \in N}$ as,
+\begin{equation}\label{eq:fb}
+\x_{k+1} = \prox_{\alpha g(\cdot, t_{k+1})} (\x_{k} - \alpha \nabla_{\x} f(\x_{k}; t_{k+1})), \quad k \in \N.
 \end{equation}
+Note that the sequence generated by~\eqref{eq:fb} could not converge in general (for a generic non-convex $f$), but it is not important for us, since we are going to regularize either the function $f$ or the algorithm $\mathcal{A}$ so to have converging sequences.
 
-Here should we formulate it in terms of functional $|f - f^*|$ instead? Let's discuss.
+In particular, we know that for a function $f$ that is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then~\eqref{eq:fb} can obtain linear convergence to the asymptotical error bound $\limsup_{k\to\infty} \|\x^*(t_{k+1}) - \x^*(t_k)\| \leq \gamma\Delta/(1-\gamma)$, with optimal $\gamma = \frac{L-m}{L+m}$; much weaker results hold for the general convex case~\cite{Simonetto20XX}.
 
-Somewhere we have to say that forward-backward may not converge in general, while here we ensure convergence since we are convex. This is an important point
-
-}
-
-\andrea{Explain a bit better what we mean by online-- I think we could be clearer?? Or maybe in the introduction.}
-
-\andrea{Is $f$ differentiable, does it have to be?}
-
-The first important and known result here is that if function $f$ is in $\mathcal{S}_{m,L}(\R^n)$ uniformly in $k$, then an online forward-backward algorithm can obtain linear convergence to the asymptotical error bound $\limsup_{k\to\infty}\|\x_k - \x^*(t_k)\| \leq \gamma\Delta/(1-\gamma)$, with optimal $\gamma = \frac{L-m}{L+m}$; much weaker results hold for the general convex case~\cite{Simonetto20XX}.
-
-The second important result is that even a simple Tikhonov regularization $+ \frac{w}{2} \|x\|^2_2$, transforming the above $f \in \mathcal{S}_{m,L}(\R^n)$ to $f' \in \mathcal{S}_{m',L'}(\R^n)$ with a better $\gamma'<\gamma$, could allow for a boost in convergence and reducing the asymptotical error.
+Another important result is that even a simple Tikhonov regularization $+ \frac{w}{2} \|x\|^2_2$, transforming the above $f \in \mathcal{S}_{m,L}(\R^n)$ to $f' \in \mathcal{S}_{m',L'}(\R^n)$ with a better $\gamma'<\gamma$, could allow for a boost in convergence and reducing the upper bound on the asymptotical error.
 In fact, if the optimizers of the true function $F = f+g$ and regularized function $F' = f'+g$ are never farther apart than $e_{\x}$, then the asymptotical error for an algorithm on $F'$ is $\gamma'\Delta'/(1-\gamma') + e_{\x}$, which can be less than the original $\gamma\Delta/(1-\gamma)$.
 
-\andrea{say something more, change above -- these are worst case bounds..?}
+\andrea{say something more, change above ..?}
 
@@
 
+\andrea{Decide $k$ or $k+1$}
+
 A slightly different approach to convex regression is to look at the algorithm directly, instead of the function.
@@
 
-\andrea{What happens to $\|\tv' - \tv''\|$ for $\x'$ and $\x''$ both interpolated? }
+\andrea{What happens to $\|\tv' - \tv''\|$ for $\x'$ and $\x''$ both interpolated? Say it has to be sequential! }
 
@@
 
-\subsection{Optional auto-tuning }
-
-\andrea{Appendix?}
-
-Discretionarily, we can also modify~\eqref{eq:operator-regression} by including $w = \zeta^2$ as an unknown of the regression problem with a penalty $c>0$, which then becomes
-\begin{equation}
-\begin{split}
-	(\hat{\tv}, \hat{w}) &= \argmin_{ \R^{n\ell} \ni \tv = [\tv_i]_{i \in I_{\ell}}, w \in (0,1)} \frac{1}{2} \sum_{i \in I_{\ell}} \norm{\tv_i - \y_i}^2 + \frac{c}{2} w^2 \\
-	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 - w \norm{\x_i - \x_j}^2 \leq 0 \ \forall i,j \in I_{\ell}, i \neq j,
-\end{split}
-\end{equation}
-this way the contraction constant does not need to be specified, and it is \emph{auto-tuned} by the regression.
+\begin{remark}[Important] We notice here that the convex regression and operator regression methods can be used with any starting function $f$, or operator $\mathcal{T}$.
+However, functions close to be in $\mathcal{S}_{m,L}(\R^n)$ (e.g., smooth $\mu$-weakly convex functions with small $\mu$) and operators close to be $\zeta$-contractive (e.g., strictly non-expansive operators) would allow for more sensible outcomes.
+A good point to make here is that the cost function of the regression problems~\eqref{socp} and \eqref{eq:operator-regression} measures the distance between the original function or operator to the class one is projecting them onto, thereby offering a proxy for regularization error.
+Moreover, one can trade-off regularization accuracy and speed tuning the free parameters $m,L$ or $\zeta$.
+An option for tuning $\zeta$ automatically is explored in the Appendix.
+\end{remark}
 
@@
 
+\subsection{Optional auto-tuning for $\zeta$ in~\eqref{eq:operator-regression}}
+
+Discretionarily, we can also modify~\eqref{eq:operator-regression} by including $w = \zeta^2$ as an unknown of the regression problem with a penalty $c>0$, which then becomes
+\begin{equation}
+\begin{split}
+	(\hat{\tv}, \hat{w}) &= \argmin_{ \R^{n\ell} \ni \tv = [\tv_i]_{i \in I_{\ell}}, w \in (0,1)} \frac{1}{2} \sum_{i \in I_{\ell}} \norm{\tv_i - \y_i}^2 + \frac{c}{2} w^2 \\
+	&\text{s.t.} \ \norm{\tv_i - \tv_j}^2 - w \norm{\x_i - \x_j}^2 \leq 0 \ \forall i,j \in I_{\ell}, i \neq j,
+\end{split}
+\end{equation}
+this way the contraction constant does not need to be specified, and it is \emph{auto-tuned} by the regression.
+
 %------------------------------------------------------------------------------

### 2021-01-16 paper/main.tex
added images

@@
 By definition $\hat{\tv}$ satisfies
-\begin{equation}
+\begin{equation}\label{eq:lipschitz-interpolation}
 	\norm{\hat{\tv} - \hat{\tv_i}} \leq \zeta \norm{\x - \x_i}, \quad \forall i \in I_{\ell},
@@
 $$
-	\psi(\xx) = \frac{1}{2(\ell-1)} \norm{\xx - \y}^2 + \psi_1(\xx)
+	\psi(\xx) = \frac{1}{2(\ell-1)} \norm{\xx - \y}^2 + \iota(\xx)
 $$
-with $\psi_1$ the indicator function imposing~\eqref{eq:interpolation-constraints} and $\xi$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}.
+\nicola{I renamed $\psi_1$ to $\iota$}
+
+with $\iota(\xx) = \sum_{e \in \mathcal{V}} \iota_{e}(\tv_{i,e},\tv_{j,e})$ and $\iota_e$ the indicator function imposing~\eqref{eq:interpolation-constraints}, and $\chi$ the indicator function imposing the ``consensus'' constraints~\eqref{eq:consensus-constraints}.
 The problem can then be solved using the Peaceman-Rachford splitting (PRS) characterized by the following updates $\ell \in \mathbb{N}$:
@@
 $$
-	\psi(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right]
+	\psi(\xx) = \sum_{e \in \mathcal{V}} \left[ \frac{1}{2 (\ell-1)} \norm{\begin{bmatrix} \tv_{i,e} \\ \tv_{j,e} \end{bmatrix} - \begin{bmatrix} \y_i \\ \y_j \end{bmatrix}}^2 + \iota_{e}(\tv_{i,e},\tv_{j,e}) \right].
 $$
-where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints} \andrea{is it $\psi_1$?}.
+%where $\iota_{e}$ denotes the indicator function of~\eqref{eq:interpolation-constraints} \andrea{is it $\psi_1$?}.
 Therefore, the update~\eqref{eq:prs-xi} can be solved by solving (possibly in parallel) the problems
@@
 \includegraphics[width = 0.9\columnwidth]{Figures/comparison_projection_methods}
-\caption{Comparison of feasibility and best approximation methods.}
+\caption{Comparison of feasibility and best approximation methods. \nicola{modified the figure to have markers}}
 \label{fig:projection_methods}
@@
 
-As we can see, MAP is by far the fastest of the methods, reaching convergence (with tolerance $10^{-14}$) in just $33$ iterations.
-Parallel projections and Peaceman-Rachford splitting reach convergence in $1930$ and $1036$ iterations, respectively, while the best approximation methods are still far from converging after $50000$ iterations.
+As we can see, MAP is by far the fastest of the methods, reaching convergence (with tolerance $10^{-14}$) in just $30$ iterations.
+Parallel projections and Peaceman-Rachford splitting reach convergence in $2161$ and $1158$ iterations, respectively, while the best approximation methods are still far from converging after $50000$ iterations.
 

### 2021-01-17 examples/online_linear_regression.py
updated examples

@@ -152,17 +152,12 @@ x_old = [x0]
 for k in range(f.time.num_samples):
     
     T_k = T.sample(k*t_s) # sampled operator
-        
-    for _ in range(num_iter):
-        
-        # Anderson acceleration on gradient
-        y = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_iter)
-        
-        # proximal step
-        y = g.proximal(y, step)
-        x_old.append(y)
+                
+    # Anderson acceleration on gradient
+    y = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_data*(num_iter-1))
     
-    x[...,k+1] = y
+    # proximal step
+    x[...,k+1] = g.proximal(y, step)
     
     # update list of past iterates
     x_old = [x[...,k+1-i] for i in range(min(k+1, m))][::-1]

### 2021-01-17 examples/phase_retrieval.py

@@ -1,0 +1,296 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+
+"""
+Solve an online phase retrieval problem.
+"""
+
+import cvxpy as cp
+import numpy as np
+from numpy import linalg as la
+from numpy.random import default_rng
+ran = default_rng()
+
+import sys
+sys.path.append("..")
+
+from tvopt.utils import orthonormal_matrix
+from tvopt import sets
+
+from reg4opt.operators import Operator, DiscreteDynamicOperator
+from reg4opt.regression import operator_regression
+from reg4opt.utils import print_progress, generate_data
+from reg4opt.solvers import anderson_acceleration
+
+
+
+class PhaseRetrieval(Operator):
+    r"""
+    Consider the phase retrieval problem
+    
+    .. math:: f(x) = \frac{1}{m} \sum_{i = 1}^m \left| \langle a_i, x \rangle^2 - b_i \right|
+    
+    where :math:`a_i \in \mathbb{R}^n` are the vectors that yield the data
+    :math:`b_i = \langle a_i, x^* \rangle^2 + e_i`, for some error :math:`e_i`.
+    
+    The operator defined by this class is 
+    :math:`\mathcal{T} y = \operatorname{prox}_{\alpha f_y}(y)` where 
+    
+    .. math:: f_y(x) = \frac{1}{m} \sum_{i = 1}^m 
+            \left| \langle a_i, y \rangle^2 + 
+            2 \langle a_i, y \rangle \langle a_i, x - y \rangle - b_i \right|
+    
+    is a linearized version of the cost function.
+    
+    See [#]_ for a treatment of the this algorithm.
+    
+    References
+    ----------
+    .. [#] D. Drusvyatskiy and A. S. Lewis, "Error Bounds, Quadratic Growth,
+           and Linear Convergence of Proximal Methods," Mathematics of Operations Research, 
+           vol. 43, no. 3, pp. 919–948, Aug. 2018.
+    """
+    
+    def __init__(self, A, b):
+        # each row in A and element of b represent a data point
+        
+        super().__init__(sets.R(A.shape[1], 1))
+        
+        self.m = A.shape[0] # domain dim. and num. data points
+        # store data as lists
[…]

### 2021-01-18 paper/main.tex
drafted simulations in paper

@@
 \newcommand{\transp}{\top}
+\newcommand{\av}{\mathbold{a}}
 \newcommand{\bv}{\mathbold{b}}
@@
 
-\andrea{Decide $k$ or $k+1$}
+\andrea{Decide $k$ or $k+1$} \nicola{we could go with $\x_{k+1}$ coming from $f_k$, which is what the learning community usually does}
 
@@
 
+\nicola{say that the algorithm applies to any operator not only forward-backward}
+
 Having to deal with composite problems $f(\cdot; t_k) + g(\cdot; t_k)$, we focus here on online algorithms of the forward-backward type, i.e., 
@@
 \begin{itemize}
-\item non-negative Least-squares
+\item non-negative Least-squares \nicola{not very interesting, the results are similar to lasso}
 
-\item L1 ?
+\item L1 \nicola{done}
 
@@
 
-\item weakly convex: time-varying phase retrival? (see Convergence of a Stochastic Gradient Method with Momentum for Nonsmooth Nonconvex Optimization)
+\item weakly convex: time-varying phase retrival? (see Convergence of a Stochastic Gradient Method with Momentum for Nonsmooth Nonconvex Optimization) \nicola{done}
 
@@
 
-%------------------------------------------------
-\subsection{Simulations set-up}
-We consider the following time-varying problem:
-\begin{equation}\label{eq:tv-problem}
-	\x^*(t_k) = \argmin_{\x \in \R^n} \frac{1}{2} \norm{\Am \x - \bv(t_k)}^2 + w \norm{\x}_1
-\end{equation}
-with $n = 10$, $\Am$ matrix with maximum and minimum (non-zero) eigenvalues $\sqrt{L} = 10^8$, $\sqrt{\mu} = 1$, and with rank $5$; $\y(t_k)$ has sinusoidal components with $3$ zero components.
-Due to $\Am$ being rank deficient, the cost $f$ is convex but not strongly so.
+In the following we present a series of experiments to evaluate the performance of the proposed methods.
+We consider the following challenging set-ups: \emph{(i)} online linear regression with a cost that has an extremely high condition number ($10^8$) and is convex but not strongly so; \emph{(ii)} an online phase retrieval problem that is weakly convex, and which is characterized by a high computational cost for an operator evaluation, \nicola{\emph{(iii)} ....}
 
 %------------------------------------------------
-\subsection{Results}
+\subsection{Online linear regression}
+In this first experiment we consider the following time-varying problem:
+\begin{equation}\label{eq:linear-regression}
+	\x^*(t_k) \in \argmin_{\x \in \R^n} \frac{1}{2} \norm{\Am \x - \bv(t_k)}^2 + w \norm{\x}_1
+\end{equation}
+with $n = 10$, $w = 5$, $\Am$ matrix with maximum and minimum (non-zero) eigenvalues $\sqrt{L} = 10^4$, $\sqrt{\mu} = 1$, and with rank $5$; $\y(t_k)$ has sinusoidal components with $3$ zero components.
+Due to $\Am$ being rank deficient, the cost $f$ is convex but not strongly so, and the condition number of the regression cost is $\kappa = L / \mu = 10^8$.
 
-%% FIGURE
-%\begin{figure}[ht]
-%\vskip 0.2in
-%\begin{center}
-%\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
-%\caption{Historical locations and number of accepted papers for International
-%Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
-%Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
-%produced, the number of accepted papers for ICML 2008 was unknown and instead
-%estimated.}
-%\label{icml-historical}
-%\end{center}
-%\vskip -0.2in
-%\end{figure}
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{Figures/lasso-operator_calls}}
+\caption{Comparison of the cumulative tracking error evolution for forward-backward, its accelerated versions FISTA \cite{beck_fast_2009} and Anderson \cite{pmlr-v119-mai20a}, OpReg-Boost and interpolated OpReg-Boost, and CvxReg-Boost.
+The methods are given a budget of $10$ gradient calls per sampling time.}
+\label{fig:lasso-operator_calls}
+\end{center}
+\vskip -0.2in
+\end{figure}
 
-%% ALGORITHM
-%\begin{algorithm}[tb]
-%   \caption{Bubble Sort}
-%   \label{alg:example}
-%\begin{algorithmic}
-%   \STATE {\bfseries Input:} data $x_i$, size $m$
-%   \REPEAT
-%   \STATE Initialize $noChange = true$.
-%   \FOR{$i=1$ {\bfseries to} $m-1$}
-%   \IF{$x_i > x_{i+1}$}
-%   \STATE Swap $x_i$ and $x_{i+1}$
-%   \STATE $noChange = false$
-%   \ENDIF
-%   \ENDFOR
-%   \UNTIL{$noChange$ is $true$}
-%\end{algorithmic}
-%\end{algorithm}
+%------------------------------------------------
+\subsection{Online phase retrieval}
+In this experiment we consider the following online phase retrieval problem \cite{duchi_stochastic_2018}
+\begin{equation}\label{eq:phase-retrieval}
+	\x^*(t_k) \in \argmin_{\x \in \R^n} \frac{1}{m} \sum_{i = 1}^{m} \left| \langle \av_i, \x \rangle^2 - b_i(t_k) \right|
+\end{equation}
+where we want to reconstruct a time-varying signal $\y(t_k)$ (which is performing a random walk on the unit sphere in $\R^n$) from the noisy measurements $b_i(t_k) = \langle \av_i, \y(t_k) \rangle^2 + \xi_i(t_k)$.
+In particular, we have $n = 15$ and $m = 200$, the measurement noises $\xi_i(t_k)$ are drawn from a Laplacian distribution of scale $1$, and $\Am = \begin{bmatrix} \av_1 & \cdots & \av_m \end{bmatrix}^\top = \mathbold{U} \mathbold{D}$ where $\mathbold{U}$ is a randomly generated orthogonal matrix and $\mathbold{D}$ is a diagonal matrix with elements equispaced in $[0, 100]$.
 
-%% TABLE
-%\begin{table}[t]
-%\caption{Classification accuracies for naive Bayes and flexible
-%Bayes on various data sets.}
-%\label{sample-table}
-%\vskip 0.15in
-%\begin{center}
-%\begin{small}
-%\begin{sc}
-%\begin{tabular}{lcccr}
-%\toprule
-%Data set & Naive & Flexible & Better? \\
-%\midrule
-%Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-%Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-%Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-%Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-%Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-%Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-%Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-%Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-%\bottomrule
-%\end{tabular}
-%\end{sc}
-%\end{small}
-%\end{center}
-%\vskip -0.1in
-%\end{table}
+We consider the prox-linear solver proposed in \cite{drusvyatskiy_error_2018} and characterized by $\T_k \y = \prox_{\alpha f_\y(\cdot; t_k)}(\y)$ where we $f_\y$ denotes the linearized version of the cost in~\eqref{eq:phase-retrieval}:
+$$
+	f_\y(\x; t_k) = \frac{1}{m} \sum_{i = 1}^m \left| \langle \av_i, \y \rangle^2 + 2 \langle \av_i, \y \rangle \langle \av_i, \x - \y \rangle - b_i \right|.
+$$
+Since we do not have a closed form expression for $\T_k$, each operator evaluation requires the solution of a quadratic program.
+
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{Figures/phase_retrieval}}
+\caption{Comparison of the cumulative tracking error evolution for prox-linear \cite{drusvyatskiy_error_2018}, the Anderson acceleration version, and OpReg-Boost.
+The methods are given a budget of $10$ operator evaluations per sampling time.}
+\label{fig:phase-retrieval}
+\end{center}
+\vskip -0.2in
+\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width = 0.9\columnwidth]{Figures/comparison_projection_methods}
-\caption{Comparison of feasibility and best approximation methods. \nicola{modified the figure to have markers}}
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{Figures/comparison_projection_methods}}
+\caption{Comparison of feasibility and best approximation methods.}
 \label{fig:projection_methods}
+\end{center}
+\vskip -0.2in
 \end{figure}
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width = 0.9\columnwidth]{Figures/MAP_histogram}
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{Figures/MAP_histogram}}
 \caption{Histogram of iterations required by MAP over $10000$ repetitions.}
 \label{fig:map-histogram}
+\end{center}
+\vskip -0.2in
 \end{figure}
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width = 0.9\columnwidth]{Figures/MAP_changing_d}
-\caption{Histogram of iterations required by MAP over $10000$ repetitions.}
+\begin{figure}[ht]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{Figures/MAP_changing_d}}
+\caption{Mean number of iterations required by MAP as a function of the number of sets, computed over $10000$ repetitions. The dashed curve depicts a logarithmic interpolation of the curve.}
 \label{fig:map-changing-d}
+\end{center}
+\vskip -0.2in
 \end{figure}

### 2021-01-18 examples/online_linear_regression.py

@@ -82,13 +82,14 @@ num_data = 5
 var = 1e-2 # for choosing training data
 
 bar_zeta = 0.5 # contraction constant of approximate operator
-bar_mu, bar_L = 1, 1e5 # strong convexity and smoothness moduli
+bar_mu, bar_L = 1, 5 # strong convexity and smoothness moduli
 
-num_iter = 5 # num. of iterations per sampled problem
+num_iter = 2 # num. of iterations per sampled problem
 
 # PRS parameters
 newton_params = {'tol':1e-4, 'num_iter':5, 'b':0.5, 'c':0.1, 'max_iter':2}
-rho = 1
+rho = 1 # for OpReg
+rho_cr = 0.01 # for CvxReg
 tol = 1.5*1e-4
 
 # parameter for Anderson acceleration (num. of past iterates in extrapolation)
@@ -154,7 +155,7 @@ for k in range(f.time.num_samples):
     T_k = T.sample(k*t_s) # sampled operator
                 
     # Anderson acceleration on gradient
-    y = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_data*(num_iter-1))
+    y = anderson_acceleration({"T":T_k}, m, x_0=x_old, num_iter=num_data*(num_iter-1)+1)
     
     # proximal step
     x[...,k+1] = g.proximal(y, step)
@@ -216,7 +217,7 @@ for k in range(f.time.num_samples):
     
     # ------ first step: solve OpReg
     # training data
-    x_i, y_i = generate_data(T_k, y, num_data, var=var)
+    x_i, y_i = generate_data(T_k, y, num_iter*num_data, var=var)
     
     # apply OpReg solver
     t_i, _ = operator_regression(x_i, y_i, bar_zeta, solver="PRS", tol=tol, rho=rho, newton_params=newton_params)
@@ -257,7 +258,7 @@ for k in range(f.time.num_samples):
         x_i, y_i, w_i = generate_data_cr(f_k, y, num_data, gradient=True, var=var)
         
         # apply OpReg solver
-        _, g_i = convex_regression(x_i, y_i, bar_mu, bar_L, w=w_i, solver="PRS", tol=tol, rho=rho, newton_params=newton_params)
+        _, g_i = convex_regression(x_i, y_i, bar_mu, bar_L, w=w_i, solver="PRS", tol=tol, rho=rho_cr, newton_params=newton_params)
         
[…]
